\documentclass[UTF8]{ctexart}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{enumitem}
\setlength{\parindent}{0pt}
\setlist[description]{style=nextline,leftmargin=0pt,labelsep=0.6em,itemsep=0.85em}

\newcommand{\vocabentry}[7]{%
\item[\textbf{#1. #2} (\textit{#3})]
#4\par
\textit{English Description}: #5\par
\textit{Example}: #6\par
\textit{Usage}: #7
}

\begin{document}
\section*{To Remember}
\begin{description}
\vocabentry{1}{speculate}{v.}{v. 推测，猜测}{to guess possible answers to a question when you do not have enough information to be certain}{I don't know why she did it - I'm just speculating.}{speculate on the cause of}
\vocabentry{2}{indignant}{adj.}{adj. 愤慨的，愤愤不平的；气愤的}{angry because of something that is wrong or not fair}{She wrote an indignant letter to the paper complaining about the council's action.}{—}
\vocabentry{3}{endeavor}{n.}{n. 尝试，努力，尽力； v. 努力，尽力}{an effort or attempt to do something}{Writing is a very different endeavor than teaching.}{—}
\vocabentry{4}{exaggerate}{v.}{v. 夸大，夸张}{to make something seem larger, more important, better, or worse than it really is}{The threat of attack has been greatly exaggerated.}{—}
\vocabentry{5}{extravagant}{adj.}{adj. 奢侈的，无节制的}{spending too much money, or using too much of something}{the extravagant lifestyle of a movie star}{extravagant of you to buy}
\vocabentry{6}{sarcastic}{adj.}{adj. 讽刺的，挖苦的，冷嘲热讽的}{using remarks that clearly mean the opposite of what you say, in order to hurt someone's feelings or to humorously criticize something}{a sarcastic comment / remark}{—}
\vocabentry{7}{deliberate}{adj.}{adj. 故意的；沉着的，小心谨慎的；从容不迫的； v. 仔细考虑；商议}{(often of something bad) intentional or planned}{a deliberate attack / insult / lie}{—}
\vocabentry{8}{manifest}{v.}{v. 使显现，使显露，表明}{to show something clearly, through signs or actions}{The workers chose to manifest their dissatisfaction in a series of strikes.}{manifest oneself in severe stomach pains}
\vocabentry{9}{intrigue}{v.}{v. 引起极大兴趣}{to interest someone a lot, especially by being strange, unusual, or mysterious}{Throughout history, people have been intrigued by the question of whether there is intelligent life elsewhere in the universe.}{intrigue by the question of}
\vocabentry{10}{intimidate}{v.}{v. 恐吓，威胁}{to frighten or threaten someone, usually in order to persuade them to do something that you want them to do}{They were intimidated into accepting a pay cut by the threat of losing their jobs.}{intimidate into accepting a pay}
\vocabentry{11}{drastic}{adj.}{adj. 极端的；激烈的；严厉的}{(especially of actions) severe and sudden or having very noticeable effects}{drastic measures}{—}
\vocabentry{12}{aggravate}{v.}{v. 使恶化，加重}{to make a bad situation worse}{Attempts to restrict parking in the city centre have further aggravated the problem of traffic congestion.}{—}
\vocabentry{13}{conspicuous}{adj.}{adj. 显而易见的}{very noticeable or attracting attention, often in a way that is not wanted}{In China, her blonde hair was conspicuous.}{—}
\vocabentry{14}{cynical}{adj.}{adj. 愤世嫉俗的；怀疑人之真诚的}{believing that people are only interested in themselves and are not sincere}{She has a pretty cynical view of men.}{cynical about politicians}
\vocabentry{15}{proximity}{n.}{n. 接近}{the state of being near in space or time}{The best thing about the location of the house is its proximity to the town centre.}{proximity to the town centre}
\vocabentry{16}{moisture}{n.}{n. 湿气}{a liquid such as water in the form of very small drops, either in the air, in a substance, or on a surface}{These plants need a rich soil that retains moisture.}{—}
\vocabentry{17}{spur}{v.}{v. 激励，鞭策；推动}{to encourage an activity or development or make it happen faster}{Rising consumer sales have the effect of spurring the economy to faster growth.}{—}
\vocabentry{18}{filter}{v.}{v. 过滤，渗透}{to appear or happen gradually or to a limited degree}{News filtered down to us during the day.}{filter through the branches}
\vocabentry{19}{fertile}{adj.}{adj. 肥沃的}{Fertile land can produce a large number of good quality crops.}{—}{—}
\vocabentry{20}{scorn}{n.}{n. 鄙视； vt. 对……不屑一顾}{a very strong feeling of no respect for someone or something that you think is stupid or has no value}{She has nothing but scorn for the new generation of politicians.}{scorn for the new generation}
\vocabentry{21}{exert}{vt.}{vt. 尽（力），运用，发挥}{to use something such as authority, power, influence, etc. in order to make something happen}{If you were to exert your influence they might change their decision.}{—}
\vocabentry{22}{authoritative}{adj.}{adj. 权威性的}{showing that you are confident, in control, and expect to be respected and obeyed}{She has an authoritative manner that at times is almost arrogant.}{—}
\vocabentry{23}{homogeneous}{adj.}{adj. 同类的，同质的，有相同特征的}{consisting of parts or people that are similar to each other or are of the same type}{a homogeneous group / society}{—}
\vocabentry{24}{versatile}{adj.}{adj. 通用的，万能的}{able to change easily from one activity to another or able to be used for many different purposes}{He's a very versatile young actor who's as happy in highbrow dramas as he is in TV comedies.}{—}
\vocabentry{25}{rupture}{n.}{n. 破裂}{an occasion when something explodes, breaks, or tears}{a rupture of the pipeline}{rupture of the pipeline}
\vocabentry{26}{chronic}{adj.}{adj. （疾病）慢性的；积习难改的；（问题）长期的}{(especially of a disease or something bad) continuing for a long time}{The study looks at adults with chronic conditions such as asthma and diabetes.}{—}
\vocabentry{27}{stride}{n.}{n. 进展，进步}{an important positive development}{The West made impressive strides in improving energy efficiency after the huge rises in oil prices during the 70s.}{stride in improving energy efficiency}
\vocabentry{28}{grieve}{v.}{v. 伤心，悲痛}{to feel or express great sadness, especially when someone dies}{He is still grieving for his wife.}{grieve for his wife}
\vocabentry{29}{elite}{n.}{n. 上层集团，掌权人物，精英； adj. 精英的，精锐的}{the richest, most powerful, best-educated, or best-trained group in a society}{the country's educated elite}{—}
\vocabentry{30}{groan}{v.}{v. 呻吟；抱怨； n. 呻吟}{to make a deep, long sound showing great pain or unhappiness}{He collapsed, groaning with pain.}{groan with pain}
\vocabentry{31}{expire}{v.}{v. 期满，（期限）终止}{If something that lasts for a fixed length of time expires, it comes to an end or stops being in use}{My passport expires next month.}{expire at the end of}
\vocabentry{32}{brim}{n.}{n. 边缘}{the bottom part of a hat that sticks out all around the head}{—}{—}
\vocabentry{33}{notion}{n.}{n. 概念，观念；观点，看法}{a belief or idea}{The show's director rejects the notion that seeing violence on television has a harmful effect on children.}{notion that seeing violence on}
\vocabentry{34}{lofty}{adj.}{adj. 极高的，巍峨的}{high}{a lofty ceiling / mountain / wall}{—}
\vocabentry{35}{allowance}{n.}{n. 限额}{money that you are given regularly, especially to pay for a particular thing}{The perks of the job include a company pension and a generous travel allowance.}{allowance from my parents}
\vocabentry{36}{reluctant}{adj.}{adj. 不情愿的}{not willing to do something and therefore slow to do it}{I was having such a good time I was reluctant to leave.}{reluctant to leave}
\vocabentry{37}{flourish}{vi.}{vi. 繁荣，兴旺}{to grow or develop successfully}{My tomatoes are flourishing this summer - it must be the warm weather.}{flourish in Britain around 1750}
\vocabentry{38}{obedient}{adj.}{adj. 服从的，顺从的}{doing, or willing to do, what you have been told to do by someone in authority}{Students are expected to be quiet and obedient in the classroom.}{obedient in the classroom}
\vocabentry{39}{notorious}{adj.}{adj. 臭名昭著的，声名狼藉的}{famous for something bad}{He is one of Mexico's most notorious criminals.}{notorious for paying its bills}
\vocabentry{40}{baffle}{v.}{v. 使困惑}{to cause someone to be completely unable to understand or explain something}{She was completely baffled by his strange behaviour.}{baffle by his strange behaviour}
\vocabentry{41}{creep}{vi.}{vi. 逐渐发生，不知不觉地出现；蔓延}{to move slowly, quietly, and carefully, usually in order to avoid being noticed}{She turned off the light and crept through the door.}{creep around outside my window}
\vocabentry{42}{revolt}{v.}{v. （使）厌恶}{If a large number of people revolt, they refuse to be controlled or ruled, and take action against authority, often violent action}{The people revolted against foreign rule and established their own government.}{revolt against foreign rule and}
\vocabentry{43}{refute}{vt.}{vt. 驳斥}{to say or prove that a person, statement, opinion, etc. is wrong or false}{to refute a person / theory / argument / claim}{—}
\vocabentry{44}{amplify}{v.}{v. 放大（声音等）}{to make something louder}{amplified music / guitar}{—}
\vocabentry{45}{propagate}{vt.}{vt. 传播，宣传； v. 繁殖，增殖}{to produce a new plant using a parent plant}{Most house plants can be propagated from stem cuttings.}{propagate from stem cuttings}
\vocabentry{46}{lodge}{n.}{n. （乡村）小屋}{a small house in the country, used especially by people on holiday or taking part in sports, or one on land belonging to a large house}{a ski / hunting lodge}{—}
\vocabentry{47}{avert}{v.}{v. 避开}{to prevent something bad from happening}{to avert a crisis / conflict / strike / famine}{—}
\vocabentry{48}{scale}{v.}{v. 按比例决定；攀登； n.规模}{to climb up a steep surface, such as a wall or the side of a mountain, often using special equipment}{The prisoner scaled the high prison wall and ran off.}{—}
\vocabentry{49}{postulate}{v.}{v. 假定……是真的}{to suggest a theory, idea, etc. as a basic principle from which a further idea is formed or developed}{It was the Greek astronomer, Ptolemy, who postulated that the earth was at the centre of the universe.}{postulate that the earth was}
\vocabentry{50}{coincidence}{n.}{n. 巧合，巧事}{an occasion when two or more similar things happen at the same time, especially in a way that is unlikely and surprising}{You chose exactly the same wallpaper as us - what a coincidence!}{coincidence that the wife of}
\vocabentry{51}{mourn}{v.}{v. 哀悼，哀伤}{to feel or express great sadness, especially because of someone's death}{Queen Victoria mourned Prince Albert/ Prince Albert's death for 40 years.}{mourn for her brother}
\vocabentry{52}{deteriorate}{vi.}{vi. 恶化}{to become worse}{She was taken into hospital last week when her condition suddenly deteriorated.}{—}
\vocabentry{53}{compensate}{v.}{v. 弥补}{to pay someone money in exchange for something that has been lost or damaged or for some problem}{Victims of the crash will be compensated for their injuries.}{compensate for their injuries}
\vocabentry{54}{deficit}{n.}{n. 缺少，缺陷}{the total amount by which money spent is more than money received, or the state of having spent more money than has been received}{The presidential candidate claims that he can cut the deficit in half within five years.}{deficit in half within five}
\vocabentry{55}{instrumental}{adj.}{adj. 重要的}{If someone or something is instrumental in a process, plan, or system, that person or thing is one of the most important influences in causing it to happen}{She was instrumental in bringing about the prison reform act.}{instrumental in bringing about the}
\vocabentry{56}{conclude}{v.}{v. 推断出}{to end a speech, meeting, or piece of writing}{She concluded the speech by remind ing us of our responsibility.}{conclude with a rousing chorus}
\vocabentry{57}{clumsy}{adj.}{adj. 笨拙的，不灵活的}{A clumsy person often has accidents because they do not behave in a careful, controlled way}{That's the third glass you've smashed this week - you're so clumsy!}{—}
\vocabentry{58}{coordinate}{v.}{v. 使协调，使一致，调整}{to make many different things work effectively as a whole}{We need someone to coordinate the whole campaign.}{—}
\vocabentry{59}{inhibit}{v.}{v. 抑制，约束}{to prevent someone from doing something by making them feel nervous or embarrassed}{Some workers were inhibited by the presence of their managers.}{inhibit by the presence of}
\vocabentry{60}{accommodate}{v.}{v. 适应；迎合，迁就}{to give what is needed to someone}{We always try to accommodate (= help) our clients with financial assistance if necessary.}{accommodate yourself：to change yourself or your behaviour to suit another person or new conditions: Some find it hard to accommodate themselves to the new working conditions. She was desperately trying to accommodate herself to her new living arrangements. At that point, I had not accommodated myself to the life of a fisherman. We tried to find a way of accommodating ourselves to a society we disliked. As a politician, he had to be able to accommodate himself to public opinion.}
\vocabentry{61}{prone}{adj.}{adj. 易于……的}{likely to show a particular characteristic, usually a negative one, or to be affected by something bad, such as damage or an illness}{I've always been prone to headaches.}{be prone to something/do something：C2 likely to show a particular characteristic, usually a negative one, or to be affected by something bad, such as damage or an illness: I've always been prone to headaches.}
\vocabentry{62}{conscientious}{adj.}{adj. 勤勤恳恳的}{putting a lot of effort into your work}{a conscientious student}{—}
\vocabentry{63}{bracket}{v.}{v. 把……归入同一类}{to put brackets around words, phrases, numbers, etc.}{I've bracketed the parts of the text that could be omitted.}{—}
\vocabentry{64}{menace}{n.}{n. 具有危险性的人（或物）； v. 威胁，威吓}{something that is likely to cause harm}{Drunk drivers are a menace to everyone.}{demand money with menaces law UK specialized：to demand money using threats: He was accused of unlawfully demanding money with menaces.}
\vocabentry{65}{tribe}{n.}{n. 部落}{a group of people, often of related families, who live together, sharing the same language, culture, and history, especially those who do not live in towns or cities}{a tribe of Amazonian Indians}{tribe of Amazonian Indians}
\vocabentry{66}{scandal}{n.}{n. 丑闻}{(an action or event that causes) a public feeling of shock and strong moral disapproval}{a financial / political / sex scandal}{scandal in the office}
\vocabentry{67}{dispute}{n.}{n. 争论，争端； v. 争执，驳斥}{an argument or disagreement, especially an official one between, for example, workers and employers or two countries with a common border}{a bitter / long-running dispute}{beyond (all) dispute：C2 so certain or true that you cannot disagree: He is beyond all dispute the finest actor in Hollywood today.； in dispute：being doubted: I don't think her ability is in dispute - what I question is her attitude.}
\vocabentry{68}{cargo}{n.}{n. 货物}{the goods carried by a ship, aircraft, or other large vehicle}{a cargo ship / plane}{cargo of wood}
\vocabentry{69}{retrospect}{n.}{n. 回顾，追溯； v. 回顾，回想，追溯}{thinking now about something in the past}{In retrospect, I think my marriage was doomed from the beginning.}{in retrospect：C2 thinking now about something in the past: In retrospect, I think my marriage was doomed from the beginning. I'm sure my university days seem happier in retrospect than they really were.}
\vocabentry{70}{layman}{n.}{n. 门外汉，外行}{someone who is part of a religious organization but who is not paid or specially trained}{—}{—}
\vocabentry{71}{susceptible}{adj.}{adj. 易受影响的}{easily influenced or harmed by something}{She isn't very susceptible to flattery.}{susceptible to flattery}
\vocabentry{72}{ascribe}{v.}{v. 把……归因于}{to be filled from Cambridge Dictionary}{—}{—}
\vocabentry{73}{rational}{adj.}{adj. 理性的，理智的}{based on clear thought and reason}{He was too upset to be rational.}{—}
\vocabentry{74}{rear}{adj.}{adj. 背面的；后面的}{at the back of something}{There's a sticker on the rear door / window.}{—}
\vocabentry{75}{preliminary}{adj.}{adj. 初步的，预备的}{coming before a more important action or event, especially introducing or preparing for it}{Preliminary results show that the vaccine is effective, but this has to be confirmed by further medical trials.}{—}
\vocabentry{76}{discern}{v.}{v. 辨别}{to see, recognize, or understand something that is not clear}{I could just discern a figure in the darkness.}{—}
\vocabentry{77}{mortgage}{n.}{n. 抵押贷款}{an agreement that allows you to borrow money from a bank or similar organization, especially in order to buy a house, or the amount of money itself}{They took out a £400,000 mortgage (= they borrowed £400,000) to buy the house.}{—}
\vocabentry{78}{omit}{v.}{v. 删去，省去，忽略}{to not include something, either by mistake or intentionally}{A list of new employees inadvertently omitted her name.}{—}
\vocabentry{79}{spontaneous}{adj.}{adj. 自发的，无意识的；自然的，天真率直的}{happening or done in a natural, often sudden way, without any planning or without being forced}{His jokes seemed spontaneous, but were in fact carefully prepared beforehand.}{—}
\vocabentry{80}{substitute}{v.}{v. 代替}{to use something or someone instead of another thing or person}{You can substitute oil for butter (= use oil instead of butter) in this recipe.}{substitute for someone/something：to perform the same job as another thing or person or to take their place: Gas-fired power stations will substitute for less efficient coal-fired equipment.}
\vocabentry{81}{restrain}{v.}{v. 制止（做）}{to control the actions or behaviour of someone by force, especially in order to stop them from doing something, or to limit the growth or force of something}{When he started fighting, it took four police officers to restrain him.}{restrain by increasing taxes}
\vocabentry{82}{harsh}{adj.}{adj. 严厉的；强烈刺眼的}{unpleasant, unkind, cruel, or more severe than is necessary}{harsh criticism}{harsh for such a minor}
\vocabentry{83}{compromise}{n.}{n. 妥协，折中； v. 使遭受危险}{an agreement in an argument in which the people involved reduce their demands or change their opinion in order to agree}{It is hoped that a compromise will be reached in today's talks.}{compromise between management and unions,}
\vocabentry{84}{incur}{v.}{v. 引起}{to experience something, usually something unpleasant, as a result of actions you have taken}{to incur debts / fines / bills}{—}
\vocabentry{85}{precipitate}{adj.}{adj. 仓促的，贸然的，轻率的}{If an action is precipitate, it is done sooner or faster than expected and without enough thought or preparation}{Don't be precipitate - think it through before you make a decision.}{—}
\vocabentry{86}{consecutive}{adj.}{adj. 连续的，连贯的}{Consecutive events, numbers, etc. follow one after another without an interruption}{This is the fifth consecutive weekend that I've spent working.}{—}
\vocabentry{87}{slack}{adj.}{adj. 懈怠的}{not tight; loose}{These tent ropes are too slack - they need tightening.}{—}
\vocabentry{88}{mediate}{v.}{v. 调解，调停，斡旋}{to talk to two separate people or groups involved in a disagreement to try to help them to agree or find a solution to their problems}{Negotiators were called in to mediate between the two sides.}{mediate between the two sides}
\vocabentry{89}{transcend}{v.}{v. 超越（经验、理性、信念等的范围），超过，超出}{to go further, rise above, or be more important or better than something, especially a limit}{The best films are those which transcend national or cultural barriers.}{—}
\vocabentry{90}{controversy}{n.}{n. 争论，辩论}{a lot of disagreement or argument about something, usually because it affects or is important to many people}{There was a big controversy surrounding /over the use of drugs in athletics.}{—}
\vocabentry{91}{explicit}{adj.}{adj. 明确的}{clear and exact}{I gave her very explicit directions how to get here.}{explicit about (= said very}
\vocabentry{92}{pedestrian}{n.}{n. 步行者，行人}{a person who is walking, especially in an area where vehicles go}{A few pedestrians sheltered from the rain in doorways.}{—}
\vocabentry{93}{denounce}{v.}{v. 谴责，斥责}{to criticize something or someone strongly and publicly}{The government's economic policy has been denounced on all sides.}{denounce on all sides}
\vocabentry{94}{constrain}{v.}{v. 限制}{to control and limit something}{The country's progress was constrained by a leader who refused to look forward.}{constrain by a leader who}
\vocabentry{95}{furious}{adj.}{adj. 愤怒的；狂怒的；猛烈的}{extremely angry}{I was late and he was furious with me.}{furious with me}
\vocabentry{96}{divine}{adj.}{adj. 神的，神圣的}{connected with a god, or like a god}{Some fans seem to regard the players as divine beings.}{—}
\vocabentry{97}{oppress}{vt.}{vt. 压迫}{to govern people in an unfair and cruel way and prevent them from having opportunities and freedom}{For years now, the people have been oppressed by a ruthless dictator.}{oppress by a ruthless dictator}
\vocabentry{98}{condemn}{v.}{v. 谴责，责备}{to criticize something or someone strongly, usually for moral reasons}{The terrorist action has been condemned as an act of barbarism and cowardice.}{condemn as an act of}
\vocabentry{99}{conviction}{n.}{n. 坚强信念}{the fact of officially being found to be guilty of a particular crime, or the act of officially finding someone guilty}{Since it was her first conviction for stealing, she was given a less severe sentence.}{conviction for stealing, she was}
\vocabentry{100}{impulse}{n.}{n. 冲动}{a sudden strong wish to do something}{I had this sudden impulse to shout out "Nonsense!" in the middle of her speech.}{on impulse (also on an impulse)：C2 because you suddenly want to, although you haven't planned to: "I didn't know you were looking for some new shoes." "Oh, I wasn't - I just bought them on impulse."}
\vocabentry{101}{pathetic}{adj.}{adj. 可怜的；不足的}{causing feelings of sadness, sympathy, or sometimes lack of respect, especially because a person or an animal is suffering}{The refugees were a pathetic sight - starving, frightened and cold.}{—}
\vocabentry{102}{haste}{n.}{n. 匆忙}{too much speed or the fact of hurrying too much}{Unfortunately the report was prepared in haste and contained several inaccuracies.}{haste to get up from}
\vocabentry{103}{impose}{v.}{v. 强制实行，强迫接受}{to officially force a rule, tax, punishment, etc. to be obeyed or received}{Very high taxes have recently been imposed on cigarettes.}{impose on cigarettes}
\vocabentry{104}{render}{v.}{v. 使成为，致使，使处于（某种状态）}{to cause someone or something to be in a particular state}{His rudeness rendered me speechless.}{—}
\vocabentry{105}{trivial}{adj.}{adj. 微不足道的}{having little value or importance}{I don't know why he gets so upset about something so trivial.}{—}
\vocabentry{106}{charter}{n.}{n. 宪章}{a formal statement of the rights of a country's people, or of an organization or a particular social group, that is agreed by or demanded from a ruler or government}{a charter of rights}{charter of rights}
\vocabentry{107}{bargain}{v.}{v. 讨价还价}{to try to make someone agree to give you something that is better for you, such as a better price or better working conditions}{Unions bargain with employers for better rates of pay each year.}{bargain with employers for better}
\vocabentry{108}{vessel}{n.}{n. 船，舰；容器；血管}{a large boat or a ship}{A warning went out to fishing vessels in the area.}{vessel in the area}
\vocabentry{109}{speciality}{n.}{n. 专长，专业}{a product that is extremely good in a particular place}{Oysters are a local speciality/a speciality of the area.}{speciality of the house (=}
\vocabentry{110}{interim}{adj.}{adj. 暂时的； n. 中间时期，过渡时期}{temporary and intended to be used or accepted until something permanent exists}{an interim solution}{—}
\vocabentry{111}{insulate}{v.}{v. 隔离，使隔绝}{to cover and surround something with a material or substance in order to stop heat, sound, or electricity from escaping or entering}{You can insulate a house against heat loss by having the windows double-glazed.}{—}
\vocabentry{112}{courtesy}{n.}{n. 礼貌}{polite behaviour, or a polite action or remark}{You might get along better with your parents if you showed them some courtesy.}{(by) courtesy of：by permission of: Jessie J appears courtesy of Universal Records. because of: He got his black eye courtesy of a bloke he insulted at the bar last night.}
\vocabentry{113}{prospective}{adj.}{adj. 有希望的，潜在的}{people who are expected to buy something, employ someone, become parents, etc.}{We've had three sets of prospective buyers looking at the house.}{prospective buyers, employers, parents, etc.：C1 people who are expected to buy something, employ someone, become parents, etc.: We've had three sets of prospective buyers looking at the house. More examples Fewer examples Given the fact that a prospective student is bombarded by prospectuses, selecting a suitable course is not easy. Her father always wants to meet her prospective boyfriends.}
\vocabentry{114}{signature}{adj.}{adj. 标志性的，惯有的}{used to refer to the special thing for which a person or place is particularly known}{The restaurant's signature dish is a seafood paella.}{—}
\vocabentry{115}{withstand}{vt.}{vt. 忍受}{to be strong enough, or not be changed by something, or to oppose a person or thing successfully}{a bridge designed to withstand earthquakes}{—}
\vocabentry{116}{indispensable}{adj.}{adj. 必不可少的}{Something or someone that is indispensable is so good or important that you could not manage without it, him, or her}{This book is an indispensable resource for researchers.}{indispensable to the talks}
\vocabentry{117}{legitimate}{adj.}{adj. 合法的，法律允许的；合理的，可接受的}{allowed by law}{The army must give power back to the legitimate government.}{—}
\vocabentry{118}{expertise}{n.}{n. 专门知识，专门技能}{a high level of knowledge or skill}{We admired the expertise with which he prepared the meal.}{expertise with which he prepared}
\vocabentry{119}{devise}{v.}{v. 设计，想出}{to invent a plan, system, object, etc., usually using your intelligence or imagination}{He's good at devising language games that you can play with students in class.}{devise by Charles M}
\vocabentry{120}{sentiment}{n.}{n. 感情；情绪}{a thought, opinion, or idea based on a feeling about a situation, or a way of thinking about something}{Nationalist sentiment has increased in the area since the bombing.}{sentiment of love and support}
\vocabentry{121}{treaty}{n.}{n. 条约}{a written agreement between two or more countries, formally approved and signed by their leaders}{a peace treaty}{treaty on European union}
\vocabentry{122}{conscience}{n.}{n. 良心，良知}{the part of you that judges how moral your own actions are and makes you feel guilty about bad things that you have done or things you feel responsible for}{He's been so kind and generous towards me recently - I think he's got a guilty conscience (= feels guilty).}{conscience at all (= does}
\vocabentry{123}{concession}{n.}{n. 让步；特许，特许权}{something that is allowed or given up, often in order to end a disagreement, or the act of allowing or giving this}{Both sides involved in the conflict made some concessions in yesterday's talks.}{concession in yesterday's talks}
\vocabentry{124}{extract}{v.}{v. 取出}{to remove or take out something}{They used to extract iron ore from this site.}{extract from olives is used}
\vocabentry{125}{monopoly}{n.}{n. 垄断；垄断商品；专卖商品}{(an organization or group that has) complete control of something, especially an area of business, so that others have no share}{The government is determined to protect its tobacco monopoly.}{monopoly of the white minority}
\vocabentry{126}{boom}{n.}{n. 繁荣； vi. 迅速发展}{a deep and loud hollow sound}{—}{—}
\vocabentry{127}{spectacular}{adj.}{adj. 壮观的，引人入胜的；n. 壮观的场面，精彩的表演}{very exciting to look at}{a spectacular view}{—}
\vocabentry{128}{pamphlet}{n.}{n. 小册子}{a thin book with only a few pages that gives information or an opinion about something}{—}{—}
\vocabentry{129}{infant}{n.}{n. 幼儿，婴儿}{a baby or a very young child}{The most important thing is for parents to spend time with their newborn infant.}{—}
\vocabentry{130}{combat}{v.}{v. 与……战斗，与……斗争}{to try to stop something unpleasant or harmful from happening or increasing}{to combat crime / terrorism / inflation / disease}{—}
\vocabentry{131}{eccentric}{adj.}{adj. 古怪的，怪僻的； n.古怪的人，怪僻的人}{strange or unusual, sometimes in a humorous way}{eccentric behaviour}{—}
\vocabentry{132}{consciousness}{n.}{n. 意识，知觉}{the state of understanding and realizing something}{Her consciousness that she's different makes her feel uneasy.}{consciousness that she's different makes}
\vocabentry{133}{protest}{n.}{n. 抗议}{a strong complaint expressing disagreement, disapproval, or opposition}{Protests have been made by many people who would be affected by the proposed changes.}{under protest：If something is done under protest, it is done unwillingly: I only went to the meeting under protest.}
\vocabentry{134}{harness}{vt.}{vt. 利用}{to put a harness on a horse, or to connect a horse to a vehicle using a harness}{—}{—}
\vocabentry{135}{aerial}{adj.}{adj. 飞机的，航空的}{in or from the air, especially from an aircraft}{Meanwhile, the massive aerial bombardment of military targets continued unabated.}{—}
\vocabentry{136}{diagnose}{v.}{v. 诊断（疾病），下诊断结论；判断（问题的原因）}{to recognize and name the exact character of a disease or a problem, by examining it}{The specialist diagnosed cancer.}{diagnose as some type of}
\vocabentry{137}{dismay}{n.}{n. 失望，沮丧； v. 使惊恐}{a feeling of unhappiness and disappointment}{Aid workers were said to have been filled with dismay by the appalling conditions that the refugees were living in.}{dismay by the appalling conditions}
\vocabentry{138}{autonomy}{n.}{n. 自主权}{the right of an organization, country, or region to be independent and govern itself}{Demonstrators demanded immediate autonomy for their region.}{autonomy for their region}
\vocabentry{139}{gossip}{n.}{n. 流言蜚语}{conversation or reports about other people's private lives that might be unkind, disapproving, or not true}{Her letter was full of gossip.}{gossip for you}
\vocabentry{140}{manipulate}{vt.}{vt. 操纵，影响}{to control something or someone to your advantage, often unfairly or dishonestly}{Throughout her career she has very successfully manipulated the media.}{—}
\vocabentry{141}{commodity}{n.}{n. 商品，货物}{a substance or product that can be traded, bought, or sold}{The country's most valuable commodities include tin and diamonds.}{—}
\vocabentry{142}{accordingly}{adv.}{adv. 相应地}{in a way that is suitable or right for the situation}{When we receive your instructions we will act accordingly.}{—}
\vocabentry{143}{gear}{v.}{v. 使适合}{to make something ready or suitable for a particular purpose}{Our program is geared to the needs of children.}{gear to the needs of}
\vocabentry{144}{redundant}{adj.}{adj. 被下岗的}{(especially of a word, phrase, etc.) unnecessary because it is more than is needed}{In the sentence "She is a single unmarried woman", the word " unmarried " is redundant.}{—}
\vocabentry{145}{league}{n.}{n. 联盟}{a group of teams playing a sport who take part in competitions between each other}{Who do you think will win the league championship this year?}{league that year}
\vocabentry{146}{discrepancy}{n.}{n. 不一致，差异，不符}{a difference between two things that should be the same}{There is some discrepancy between the two accounts.}{discrepancy between the two accounts}
\vocabentry{147}{exclude}{vt.}{vt. 不包括，未包括；排挤，排除}{to prevent someone or something from entering a place or taking part in an activity}{Women are still excluded from the club.}{exclude from the club}
\vocabentry{148}{imitation}{n.}{n. 模仿}{an occasion when someone or something imitates another person or thing}{Ten-year-olds have started wearing lipstick and make-up in imitation of the older girls.}{imitation of the older girls}
\vocabentry{149}{interior}{adj.}{adj. 内政的，内务的}{inside}{The interior walls have patches of damp on them.}{—}
\vocabentry{150}{proportion}{n.}{n. 比例}{the number or amount of a group or part of something when compared to the whole}{Children make up a large proportion of the world's population.}{proportion of the world's population}
\vocabentry{151}{successive}{adj.}{adj. 连续的}{happening one after the other without any break}{It was the team's fourth successive defeat.}{—}
\vocabentry{152}{economical}{adj.}{adj. 划算的}{using as little of something as possible; wasting nothing or very little}{People were urged to be economical with water as a drought was declared.}{economical with the truth：humorous avoiding stating the true facts about a situation, or lying about it: Anyone who tells you that this is a simple process is being economical with the truth.}
\vocabentry{153}{metropolitan}{adj.}{adj. 大城市的，大都会的}{relating to or being a large city}{the Metropolitan Museum of Art in New York}{—}
\vocabentry{154}{net}{adj.}{adj. 纯利的，净值的，净的}{left when there is nothing else to be taken away}{I earn \$50,000 gross, but my net income (= income that is left after tax has been paid) is about \$36,000.}{—}
\vocabentry{155}{spacious}{adj.}{adj. 宽敞的，广阔的}{large and with a lot of space}{a spacious house / living room}{—}
\vocabentry{156}{embody}{v.}{v. 体现，象征}{to represent a quality or an idea exactly}{She embodied good sportsmanship on the playing field.}{—}
\vocabentry{157}{specify}{v.}{v. 详细说明}{to explain or describe something clearly and exactly}{He said we should meet but didn't specify a time.}{—}
\vocabentry{158}{drain}{n.}{n. 消耗，耗竭}{a pipe or channel that is used to carry away waste matter and water from a building, or an opening in the road that rain water can flow down}{I think the kitchen drain is blocked.}{drains [ plural ] UK：the system of pipes, openings in the ground, or other devices that are used for carrying away waste matter and water: There was an unpleasant smell coming from the drains.}
\vocabentry{159}{pastime}{n.}{n. 消遣，娱乐}{an activity that is done for enjoyment}{Do-it-yourself is the nation's most popular pastime.}{—}
\vocabentry{160}{symmetry}{n.}{n. 对称（性）；均衡}{the quality of having parts that match each other, especially in a way that is attractive, or similarity of shape or contents}{The design of the house had a pleasing symmetry, its oblong shape being picked up in its elongated windows.}{—}
\vocabentry{161}{utilize}{v.}{v. 使用}{to use something in an effective way}{The vitamins come in a form that is easily utilized by the body.}{utilize by the body}
\vocabentry{162}{hierarchy}{n.}{n. 阶层，等级制度}{a system in which people or things are arranged according to their importance}{Some monkeys have a very complex social hierarchy.}{hierarchy to become party leader}
\vocabentry{163}{neutral}{adj.}{adj. 中立的}{not saying or doing anything that would encourage or help any of the groups involved in an argument or war}{If there's an argument between my daughter and her mother, it's important that I remain neutral.}{—}
\vocabentry{164}{disperse}{v.}{v. 分散，散开}{to spread across or move away over a large area, or to make something do this}{When the rain came down the crowds started to disperse.}{—}
\vocabentry{165}{symposium}{n.}{n. 专题报告会}{an occasion at which people who have great knowledge of a particular subject meet in order to discuss a matter of interest}{a symposium on European cinema}{symposium on European cinema}
\vocabentry{166}{counterpart}{n.}{n. 对应的人（物）}{a person or thing that has the same purpose as another one in a different place or organization}{The prime minister is to meet his European counterparts to discuss the war against drugs.}{counterpart to discuss the war}
\vocabentry{167}{erroneous}{adj.}{adj. 错误的}{wrong or false}{an erroneous belief / impression}{—}
\vocabentry{168}{namely}{adv.}{adv. 即，也就是}{used when you want to give more detail or be more exact about something you have just said}{We need to get more teachers into the classrooms where they're most needed, namely in high poverty areas.}{namely in high poverty areas}
\vocabentry{169}{attentive}{adj.}{adj. 专心的，注意的}{listening carefully}{an attentive audience}{—}
\vocabentry{170}{depute}{vt.}{vt. 把（工作、责任等）交托给}{to ask someone to act or speak for you}{I've deputed Lara Brown to speak for me at the conference.}{depute something to someone：If you depute something to someone, you ask them to do it for you: She's deputing the organization of the exhibition to Sara.}
\vocabentry{171}{pose}{vt.}{vt. 引起，导致，造成；假扮，冒充； n. 姿势}{to pretend to be something that you are not or to have qualities that you do not have, in order to be admired or attract interest}{He doesn't really know a thing about the theatre - he's just posing!}{—}
\vocabentry{172}{avail}{n.}{n. 益处}{use, purpose, advantage, or profit}{We tried to persuade her not to resign, but to no avail (= did not succeed).}{—}
\vocabentry{173}{acquaint}{v.}{v. 使熟悉}{to be filled from Cambridge Dictionary}{—}{—}
\vocabentry{174}{distil}{v.}{v. 蒸馏，用蒸馏法提取}{to make a liquid stronger or purer by heating it until it changes to a gas and then cooling it so that it changes back into a liquid}{Some strong alcoholic drinks such as whisky are made by distilling.}{—}
\vocabentry{175}{controversial}{adj.}{adj. 有争议的}{causing disagreement or discussion}{a controversial issue / decision / speech / figure}{—}
\vocabentry{176}{misery}{n.}{n. 痛苦，悲惨，不幸}{great unhappiness}{We have witnessed the most appalling scenes of human misery.}{—}
\vocabentry{177}{dictate}{v.}{v. 决定，支配}{to give orders, or tell someone exactly what they must do, with total authority}{The UN will dictate the terms of troop withdrawal from the region.}{dictate that only running shoes}
\vocabentry{178}{sacrifice}{n.}{n. 牺牲； v. 牺牲}{the act of giving up something that is valuable to you in order to help someone else}{We had to make sacrifices in order to pay for our children's education.}{sacrifice in order to pay}
\vocabentry{179}{veto}{v.}{v. 否决}{to refuse to allow something}{In 1961, President De Gaulle vetoed the UK's entry into the Common Market.}{—}
\vocabentry{180}{split}{v.}{v. 分配； adj. 分裂的}{to (cause to) divide into two or more parts, especially along a particular line}{The prize was split between Susan and Kate.}{split the difference：If you split the difference, you agree on a number or amount that is exactly in the middle of the difference between two other numbers or amounts: I suggested that we split the difference between his current salary and what we had initially offered for the job. to accept that you will reduce your demands or change your opinion in order to reach an agreement with someone: She is always trying to split the difference and please everyone.}
\vocabentry{181}{brutal}{adj.}{adj. 残忍的，粗鲁的}{cruel, violent, and completely without feelings}{a brutal dictator}{—}
\vocabentry{182}{lag}{v.}{v. 落后，滞后}{to move or make progress so slowly that you are behind other people or things}{He's lagging behind - I think we'd better wait for him to catch us up.}{—}
\vocabentry{183}{offspring}{n.}{n. 后代；（动物的）崽}{the young of an animal}{In the case of the guinea pig, the number of offspring varies between two and five.}{—}
\vocabentry{184}{dial}{v.}{v. 拨（电话号码）}{to operate a phone or make a phone call to someone by choosing a particular series of numbers on the phone}{Can I dial this number direct, or do I have to go through the operator?}{—}
\vocabentry{185}{prevalent}{adj.}{adj. 普遍的，流行的}{existing very commonly or happening often}{These diseases are more prevalent among young children.}{prevalent among young children}
\vocabentry{186}{resemble}{vt.}{vt. 像；类似，相似}{to look like or be like someone or something}{You resemble your mother very closely.}{—}
\vocabentry{187}{brittle}{adj.}{adj. 易碎的}{delicate and easily broken}{As you get older your bones become increasingly brittle.}{—}
\vocabentry{188}{stroke}{n.}{n. 中风}{a sudden change in the blood supply to a part of the brain, sometimes causing a loss of the ability to move particular parts of the body}{When a massive stroke left my father paralysed on his left side, no one thought he'd ever walk again.}{stroke that left her unable}
\vocabentry{189}{retreat}{n.}{n. 躲藏处}{a move back by soldiers or an army, either because they have been defeated or in order to avoid fighting}{the retreat from Dunkirk}{retreat from Dunkirk}
\vocabentry{190}{foster}{v.}{v. 培养；促进}{to take care of a child, usually for a limited time, without being the child's legal parent}{Would you consider fostering a child?}{foster to help children who}
\vocabentry{191}{alike}{adv.}{adv. 同样都； adj. 相同的，类似的}{in a similar way}{The twins even dress alike.}{—}
\vocabentry{192}{sanction}{n.}{n. 批准； v. 批准；支持；对……实施制裁}{an official order, such as the stopping of trade, that is taken against a country in order to make it obey international law}{Many nations have imposed sanctions on the country because of its attacks on its own people.}{sanction on the country because}
\vocabentry{193}{intuition}{n.}{n. 直觉}{(knowledge from) an ability to understand or know something immediately based on your feelings rather than facts}{Often there's no clear evidence one way or the other and you just have to base your judgment on intuition.}{intuition that you'd been involved}
\vocabentry{194}{entail}{v.}{v. 导致}{to make something necessary, or to involve something}{Such a large investment inevitably entails some risk.}{—}
\vocabentry{195}{provocative}{adj.}{adj. 挑衅的，煽动的，刺激的}{causing thought about interesting subjects}{The programme will take a detailed and provocative look at the problem of homelessness.}{—}
\vocabentry{196}{nominal}{adj.}{adj. 名义上的；象征性的，很少的；名词性的}{in name or thought but not in fact or not as things really are}{She's the nominal head of our college - the real work is done by her deputy.}{—}
\vocabentry{197}{divert}{v.}{v. 改变；转移，转移…的注意力}{to cause something or someone to change direction}{Traffic will be diverted through the side streets while the main road is resurfaced.}{divert through the side streets}
\vocabentry{198}{shabby}{adj.}{adj. 破烂的}{looking old and in bad condition because of being used for a long time or not being cared for}{He wore a shabby old overcoat.}{—}
\vocabentry{199}{brood}{v.}{v. 冥思苦想}{to think for a long time about things that make you sad, worried, or angry}{I wish she wouldn't sit brooding in her room all day.}{brood in her room all}
\vocabentry{200}{inspection}{n.}{n. 检查，细看}{the act of looking at something carefully, or an official visit to a building or organization to check that everything is correct and legal}{Her passport seemed legitimate, but on closer inspection, it was found to have been altered.}{inspection of the building}
\vocabentry{201}{curse}{n.}{n. 诅咒}{magic words that are intended to bring bad luck to someone}{In the story, a wicked witch puts a curse on the princess for a hundred years.}{curse on the princess for}
\vocabentry{202}{dynamic}{n.}{n. 动力}{the relationship between two or more people and the way that they feel about and behave towards each other, especially when this can change}{Each individual holds the power to influence the group dynamic.}{dynamics：[ plural ] forces or processes that produce change inside a group or system: The fight for the leadership gave a fascinating insight into the group's dynamics. Managers and investors need to understand these market dynamics. Infidelity by one parent can alter the dynamics of a whole family. [ plural ] physics specialized forces that produce movement: This software is used for modelling atmospheric dynamics. Do we understand the dynamics of how the rings around a planet are formed or held together? [ U ] physics specialized the scientific study of the forces that produce movement: fluid dynamics She is is particularly interested in an area of fluid dynamics concerned with spray. Orthogonal matrices are of very great importance in dynamics. [ plural ] music specialized changes in loudness in a piece of music: The piece is full of abrupt shifts in theme, mood, and dynamics. Remember to pay attention to the tempo, time signature, and dynamics. More examples Fewer examples From the outside, we can't know the dynamics inside the campaign. He is an experienced financial economist with expertise in the dynamics of the residential property market. This article explores the role of team dynamics in the evolution of small businesses. The rhythms were stark and choppy, and the dynamics strong.}
\vocabentry{203}{incidence}{n.}{n. 发生率}{the rate at which something, especially a disease, happens}{They found an increased incidence of cancer near nuclear power stations.}{incidence of cancer near nuclear}
\vocabentry{204}{consensus}{n.}{n. 一致同意}{a generally accepted opinion or decision among a group of people}{The general consensus in the office is that he can't do his job.}{consensus in the office is}
\vocabentry{205}{incorporate}{v.}{v. 包含；使并入}{to include something as part of something larger}{The European Convention of Human Rights has been incorporated into Irish law.}{incorporate into Irish law}
\vocabentry{206}{conscious}{adj.}{adj. 意识到的；有意的}{to notice that a particular thing or person exists or is present}{My tooth doesn't exactly hurt, but I'm conscious of it (= I can feel it) all the time.}{be conscious of something/someone：B2 to notice that a particular thing or person exists or is present: My tooth doesn't exactly hurt, but I'm conscious of it (= I can feel it) all the time.}
\vocabentry{207}{hasty}{adj.}{adj. 匆忙的}{Hasty actions are done in a hurry, sometimes without the necessary care or thought}{He warned against making hasty decisions.}{hasty in judging him}
\vocabentry{208}{hence}{adv.}{adv. 因此}{that is the reason or explanation for}{His mother was Italian, hence his name - Luca.}{—}
\vocabentry{209}{proclaim}{v.}{v. 声明，声称}{to announce something publicly or officially, especially something positive}{All the countries have proclaimed their loyalty to the alliance.}{proclaim that socialism was dead}
\vocabentry{210}{skeptical}{adj.}{adj. 表示怀疑的}{doubting that something is true or useful}{Many experts remain skeptical about/of his claims.}{—}
\vocabentry{211}{venture}{n.}{n. 企业，项目}{a new activity, usually in business, that involves risk or uncertainty}{She advised us to look abroad for more lucrative business ventures.}{venture between American and Japanese}
\vocabentry{212}{apt}{adj.}{adj. 有做某事的倾向}{suitable or right for a particular situation}{an apt comment / description}{—}
\vocabentry{213}{manual}{adj.}{adj. 手工的；体力的}{done with the hands}{the manual sorting of letters}{—}
\vocabentry{214}{snap}{v.}{v. 拍照，摄影； n. 快照}{to cause something that is thin to break suddenly and quickly with a cracking sound}{You'll snap that ruler if you bend it too far.}{snap that ruler if you}
\vocabentry{215}{ratio}{n.}{n. 比率，比例}{the relationship between two groups or amounts that expresses how much bigger one is than the other}{The ratio of men to women at the conference was ten to one/10:1.}{ratio of men to women}
\vocabentry{216}{disposition}{n.}{n. 排列，部署}{the particular type of character that a person naturally has}{She is of a nervous / cheerful / sunny disposition.}{—}
\vocabentry{217}{provision}{n.}{n. （法律等的）条款；供应}{the act of providing something}{The provision of good public transport will be essential for developing the area.}{provisions [ plural ]：supplies of food and other necessary things: provisions for the journey}
\vocabentry{218}{offensive}{adj.}{adj. 冒犯的，无礼的}{causing offence}{This programme contains language that some viewers might find offensive.}{—}
\vocabentry{219}{prime}{adj.}{adj. 典型的，有代表性的；最好的，一流的}{main or most important}{This is a prime example of 1930s architecture.}{—}
\vocabentry{220}{warrant}{v.}{v. 使……有必要； n. 凭证}{to make a particular activity necessary}{Obviously what she did was wrong, but I don't think it warranted such a severe punishment.}{—}
\vocabentry{221}{portray}{v.}{v. 描绘；描述；扮演}{to represent or describe someone or something in a painting, film, book, or other artistic work}{The painting portrays a beautiful young woman in a blue dress.}{portray someone as something：If a person in a film, book, etc. is portrayed as a particular type of character, they are represented in that way: The father in the film is portrayed as a fairly unpleasant character.}
\vocabentry{222}{accordance}{n.}{n. 按照，依据}{following or obeying a rule, law, wish, etc.}{In accordance with her wishes, she was buried in France.}{in accordance with a rule, law, wish, etc.：C1 following or obeying a rule, law, wish, etc.: In accordance with her wishes, she was buried in France. Thesaurus: synonyms, antonyms, and examples according to the law, rules, etc. according to If we do not act according to the rules laid down for such cases, there will be chaos. in line with What she did was not always completely in line with the law. in accordance with The council has not acted in accordance with its obligations. obey If they don't obey the rules, they will be asked to leave. follow We are obliged to follow the law in this matter. See more results »}
\vocabentry{223}{blaze}{n.}{n. 烈火，大火}{a large, strong fire}{Firefighters took two hours to control the blaze.}{—}
\vocabentry{224}{prominent}{adj.}{adj. 突出的，杰出的}{very well known and important}{a prominent Democrat}{—}
\vocabentry{225}{scrutiny}{n.}{n. 细看，详细检查，仔细观察}{the careful and detailed examination of something in order to get information about it}{The government's record will be subjected to/come under (close) scrutiny in the weeks before the election.}{scrutiny in the weeks before}
\vocabentry{226}{confidential}{adj.}{adj. 机密的}{secret or private, often in a formal, business, or military situation}{All information will be treated as strictly confidential.}{—}
\vocabentry{227}{liability}{n.}{n. 责任}{the fact that someone is legally responsible for something}{He denies any liability for the damage caused.}{liabilities [ plural ] finance \& economics specialized：debts: The business has liabilities of 2 million euros.}
\vocabentry{228}{reciprocal}{adj.}{adj. 相互的，互惠的}{A reciprocal action or arrangement involves two people or groups of people who behave in the same way or agree to help each other and give each other advantages.}{—}{—}
\vocabentry{229}{empirical}{adj.}{adj. 实证的，以观察或实验为根据的}{based on what is experienced or seen rather than on theory}{This theory needs to be backed up with solid empirical evidence.}{—}
\vocabentry{230}{forum}{n.}{n. 论坛}{a situation or meeting in which people can talk about a problem or matter especially of public interest}{a forum for debate / discussion}{forum for debate / discussion}
\vocabentry{231}{absurd}{adj.}{adj. 荒谬的}{stupid and unreasonable, or silly in a humorous way}{What an absurd thing to say!}{the absurd：things that happen that are stupid or unreasonable: border on the absurd The whole situation borders on the absurd. She has a keen sense of the absurd.}
\vocabentry{232}{irony}{n.}{n. 反语}{a situation in which something which was intended to have a particular result has the opposite or a very different result}{The irony is that the new tax system will burden those it was intended to help.}{irony of becoming a hero}
\vocabentry{233}{executive}{n.}{n. 经理； adj. 执行的}{someone in a high position, especially in business, who makes decisions and puts them into action}{She is now a senior executive, having worked her way up through the company.}{the executive：the part of a government that is responsible for making sure that laws and decisions are put into action}
\vocabentry{234}{ridiculous}{adj.}{adj. 可笑的，荒谬的}{stupid or unreasonable and deserving to be laughed at}{Do I look ridiculous in this hat?}{ridiculous in this hat}
\vocabentry{235}{assimilate}{v.}{v. 融入}{to become part of a group, country, society, etc., or to make someone or something become part of a group, country, society, etc.}{The European Union should remain flexible enough to assimilate more countries quickly.}{assimilate into an alien culture}
\vocabentry{236}{presumably}{adv.}{adv. 大概，据推测，可能}{used to say what you think is the likely situation}{They can presumably afford to buy a bigger apartment.}{—}
\vocabentry{237}{eclipse}{n.}{n. 日食，月蚀； v. 掩盖……的重要性；使暗淡}{an occasion when the sun disappears from view, either completely or partly, while the moon is moving between it and the earth, or when the moon becomes darker while the shadow of the earth moves over it}{Some people believe that a solar / lunar eclipse affects their relationships, energy levels, and mood.}{eclipse of the sun}
\vocabentry{238}{prestige}{n.}{n. 威望，声望}{respect and admiration given to someone or something, usually because of a reputation for high quality, success, or social influence}{The company has gained international prestige.}{prestige of working for a}
\vocabentry{239}{primarily}{adv.}{adv. 主要地}{mainly}{We're primarily concerned with keeping expenditure down.}{—}
\vocabentry{240}{constitution}{n.}{n. 宪法，章程}{the set of political principles by which a state or organization is governed, especially in relation to the rights of the people it governs}{Britain has no written constitution.}{constitution of the United States}
\vocabentry{241}{subtle}{adj.}{adj. 不明显的，微妙的；难以捉摸的；精巧的，精妙的}{not loud, bright, noticeable, or obvious in any way}{The room was painted a subtle shade of pink.}{subtle to be understood by}
\vocabentry{242}{collision}{n.}{n. 碰撞；冲突}{an accident that happens when two vehicles hit each other with force}{There has been a collision on the southbound stretch of the motorway.}{collision on the southbound stretch}
\vocabentry{243}{shepherd}{n.}{n. 牧羊人}{a person whose job is to take care of sheep and move them from one place to another}{a shepherd boy}{—}
\vocabentry{244}{chamber}{n.}{n. （作特殊用途的）房间}{a room used for a special or official purpose, or a group of people who form (part of) a parliament}{Meetings of the council are held in the council chamber.}{in chambers law specialized：If a trial is in chambers, it happens in a court room without the public, newspaper reporters, etc. being there: They agreed to maintain confidentiality by holding the hearings in chambers but having the judgments read in open court.}
\vocabentry{245}{agony}{n.}{n. 极大的痛苦}{extreme physical or mental pain or suffering}{She lay there screaming in agony.}{agony of suspense}
\vocabentry{246}{striking}{adj.}{adj. 突出的，惊人的，异常的}{very unusual or easily noticed, and therefore attracting a lot of attention}{She bears a striking resemblance to her mother.}{—}
\vocabentry{247}{retrieve}{v.}{v. 取回，重新得到，挽回；检索}{to find and bring back something}{We taught our dog to retrieve a ball.}{—}
\vocabentry{248}{adequate}{adj.}{adj. 足够的，充分的}{enough or satisfactory for a particular purpose}{It's not a big salary but it's adequate for our needs.}{adequate for our needs}
\vocabentry{249}{corrupt}{adj.}{adj. 腐败的}{dishonestly using your position or power to get an advantage, especially for money}{Both companies are under investigation for corrupt practices.}{—}
\vocabentry{250}{bewilder}{v.}{v. 使不知所措；使迷惑}{to confuse someone}{The instructions completely bewildered me.}{—}
\vocabentry{251}{duplicate}{v.}{v. 重复；复制}{to make an exact copy of something}{The documents had been duplicated.}{—}
\vocabentry{252}{likelihood}{n.}{n. 可能性}{the chance that something will happen}{This latest dispute greatly increases the likelihood of a strike.}{in all likelihood：C2 almost certainly: In all likelihood, everything will go to plan.}
\vocabentry{253}{lest}{conj.}{conj. 惟恐；以免；担心}{in order to prevent any possibility that something will happen}{They were afraid to complain about the noise lest they annoyed the neighbours.}{—}
\vocabentry{254}{premise}{n.}{n. 前提}{an idea or theory on which a statement or action is based}{They had started with the premise that all men are created equal.}{premise that all men are}
\vocabentry{255}{wretched}{adj.}{adj. 可怜的；身心疲惫的}{unpleasant or of low quality}{a wretched childhood}{—}
\vocabentry{256}{penalty}{n.}{n. 惩罚，处罚}{a punishment, or the usual punishment, for doing something that is against a law}{They asked for the maximum penalty for hoax calls to be increased to one year.}{penalty for hoax calls to}
\vocabentry{257}{ministry}{n.}{n. （政府的）部，内阁}{in Britain and some other countries, a department of the government led by a minister}{the Ministry of Defence/Agriculture}{ministry of Defence/Agriculture}
\vocabentry{258}{unusually}{adv.}{adv. 非常}{more than is usual or expected, or in a way that is not usual}{He was unusually polite.}{unusually for someone：C2 in a way that is not usual for someone: Unusually for me, I felt deeply embarrassed.}
\vocabentry{259}{remedy}{n.}{n. 补救}{a successful way of curing an illness or dealing with a problem or difficulty}{an effective herbal remedy for headaches}{legal remedy law specialized：a way of solving a problem or ordering someone to make a payment for harm or damage they have caused, using a decision made in a law court: legal remedy for We have exhausted all possible legal remedies for this injustice.}
\vocabentry{260}{strive}{v.}{v. 努力，奋斗}{to try very hard to do something or to make something happen, especially for a long time or against difficulties}{Mr Roe has kindled expectations that he must now strive to live up to.}{strive to live up to}
\vocabentry{261}{cathedral}{n.}{n. 大教堂}{a very large, usually stone, building for Christian worship. It is the largest and most important church of a diocese}{Salisbury Cathedral}{—}
\vocabentry{262}{exclusively}{adv.}{adv. 特定地；仅仅}{only}{This offer is available exclusively to our established customers.}{exclusively to our established customers}
\vocabentry{263}{extinguish}{v.}{v. 熄灭，扑灭}{to stop a fire or a light burning}{It took the firefighters several hours to extinguish the flames.}{—}
\vocabentry{264}{allege}{v.}{v. 断言}{to say that someone has done something illegal or wrong without giving proof}{The two men allege (that) the police forced them to make false confessions.}{allege to have been at}
\vocabentry{265}{scrape}{v.}{v. 刮擦，（使）发出刮擦声}{to remove an unwanted covering or a top layer from something, especially using a sharp edge or something rough}{Scrape your boots clean before you come in.}{—}
\vocabentry{266}{refrain}{vi.}{vi. 克制，抑制；避免}{to avoid doing or stop yourself from doing something}{We refrained from talk ing until we knew that it was safe.}{refrain from talk ing until}
\vocabentry{267}{tyre}{n.}{n. 轮胎，车胎}{a thick rubber ring, often filled with air, that is fitted around the outer edge of the wheel of a vehicle, allowing the vehicle to stick to the road surface and to travel over the ground more easily}{I've got a flat tyre (= the air has gone out of it).}{tyre in the back of}
\vocabentry{268}{threshold}{n.}{n. 门槛；开端}{the floor of an entrance to a building or room}{—}{—}
\vocabentry{269}{sufficiently}{adv.}{adv. 充分地}{enough}{McGeechan has not recovered sufficiently to play in the semifinal tomorrow.}{sufficiently to play in the}
\vocabentry{270}{rein}{v.}{v. 控制}{a long, thin piece of material, especially leather, that helps you to control and direct a horse}{You pull on both reins to stop or slow a horse, but only the left rein to turn left.}{rein to turn left}
\vocabentry{271}{propaganda}{n.}{n. 宣传；宣传方法}{information, ideas, opinions, or images, often only giving one part of an argument, that are broadcast, published, or in some other way spread with the intention of influencing people's opinions}{political / wartime propaganda}{—}
\vocabentry{272}{circulation}{n.}{n. 流传，传播}{the process in which something such as information, money, or goods passes from one person to another}{Police have warned that there are a lot of fake £50 notes in circulation.}{—}
\vocabentry{273}{correspondent}{n.}{n. 通讯员，记者}{a person employed by a newspaper, a television station, etc. to report on a particular subject or send reports from a foreign country}{a war correspondent}{correspondent for the Guardian}
\vocabentry{274}{bribe}{v.}{v. 向……行贿}{to try to make someone do something for you by giving them money, presents, or something else that they want}{He bribed immigration officials and entered the country illegally.}{—}
\vocabentry{275}{exempt}{adj.}{adj. 被免除的}{with special permission not to do or pay something}{Goods exempt from this tax include books and children's clothes.}{exempt from this tax include}
\vocabentry{276}{assignment}{n.}{n. （课外）作业}{a piece of work given to someone, typically as part of their studies or job}{a freelance / photo assignment}{on assignment：Someone who is on assignment is doing a particular job or piece of work, usually in a particular place where they have been sent for a period of time: Both journalists were killed while on assignment in the region.}
\vocabentry{277}{illusion}{n.}{n. 假象，幻象}{an idea or belief that is not true}{I'm under no illusions (= I understand the truth) about the man I married.}{illusion about his talents as}
\vocabentry{278}{readily}{adv.}{adv. 乐意地；容易地}{quickly, immediately, willingly, or without any problem}{He readily agreed to help.}{—}
\vocabentry{279}{reservation}{n.}{n. 保留意见}{an arrangement in which something such as a seat on an aircraft or a table at a restaurant is kept for you}{I'd like to make a table reservation for two people for nine o'clock.}{reservation for two people for}
\vocabentry{280}{tumble}{v.}{v. （使）跌倒，摔下；（价格等）暴跌； n. 跌倒，摔跤}{to fall quickly and without control}{I lost my footing and tumbled down the stairs.}{tumble over}
\vocabentry{281}{practicable}{adj.}{adj. 能实行的，行得通的}{able to be done or put into action}{The troops will be brought home as soon as practicable.}{practicable to complete the tunnel}
\vocabentry{282}{publication}{n.}{n. 出版，发行}{the act of making information or stories available to people in a printed or electronic form}{The brochure will be ready for publication in September.}{publication in September}
\vocabentry{283}{degenerate}{v.}{v. 堕落，衰减； adj. 腐化的，颓废的； n. 堕落者}{to become worse in quality}{Educational standards are degenerating year by year because of a lack of funds.}{degenerate into violence}
\vocabentry{284}{massive}{adj.}{adj. 大规模的；巨大的；大量的；非常严重的}{very large in size, amount, or number}{They have a massive house.}{—}
\vocabentry{285}{endure}{v.}{v. 持续存在；忍受，容忍}{to suffer something difficult, unpleasant, or painful}{We had to endure a nine-hour delay at the airport.}{—}
\vocabentry{286}{locomotive}{n.}{n. 机车，火车头}{the engine of a train}{—}{—}
\vocabentry{287}{interpret}{v.}{v. 解读；解释}{to decide what the meaning of something is}{It's difficult to interpret these statistics without knowing how they were obtained.}{—}
\vocabentry{288}{expel}{v.}{v. 驱逐}{to force someone to leave a school, organization, or country}{The new government has expelled all foreign diplomats.}{—}
\vocabentry{289}{envisage}{v.}{v. 想象，设想}{to imagine or expect something in the future, especially something good}{Train fare increases of 15 percent are envisaged for the next year.}{envisage for the next year}
\vocabentry{290}{tap}{v.}{v. 开发，发掘}{to get or make use of something}{For more than a century, Eastern cities have expanded their water supplies by tapping ever more remote sources.}{—}
\vocabentry{291}{correlate}{v.}{v. （使）相关联}{If two or more facts, numbers, etc. correlate or are correlated, there is a relationship between them}{Stress levels and heart disease are strongly correlated (= connected).}{—}
\vocabentry{292}{diploma}{n.}{n. 毕业文凭，毕业证书}{a qualification given by a college or university to show that you have passed a particular exam or finished your studies}{a diploma in business studies}{diploma in business studies}
\vocabentry{293}{condense}{v.}{v. 精炼}{to reduce something, such as a speech or piece of writing, in length}{I condensed ten pages of comments into/to two.}{—}
\vocabentry{294}{consolidate}{v.}{v. 巩固，加强}{to become, or cause something to become, stronger, and more certain}{The success of their major product consolidated the firm's position in the market.}{—}
\vocabentry{295}{fatigue}{n.}{n. 疲乏，劳累}{extreme tiredness}{She was suffering from fatigue.}{—}
\vocabentry{296}{cope}{vi.}{vi. 处理，应对}{to deal successfully with a difficult situation}{It's only been a year since he died - how's she coping (= how is she)?}{cope with four children under}
\vocabentry{297}{tender}{adj.}{adj. 年幼的，未成熟的}{gentle, loving, or kind}{a tender look / smile}{—}
\vocabentry{298}{concede}{v.}{v. 承认}{to admit, often unwillingly, that something is true}{The government has conceded (that) the new tax policy has been a disaster.}{—}
\vocabentry{299}{timber}{n.}{n. 木料}{trees that are grown so that the wood from them can be used for building}{a timber forest}{—}
\vocabentry{300}{sake}{n.}{n. 理由}{in order to help or bring advantage to someone}{Please do it, for David's sake.}{for the sake of someone /for someone's sake：B2 in order to help or bring advantage to someone: Please do it, for David's sake. Their parents only stayed together for the sake of the children. I hope for both our sakes that you're right! More examples Fewer examples I'm trying to keep life normal for the sake of my two boys. They were very unhappily married but kept up appearances for the sake of their children. I hope for your sake that she's happy with the arrangements. I hope he's there for Paul's sake. I knew I had to stay calm for Maria's sake.}
\vocabentry{301}{adhere}{v.}{v. 坚持}{to stick firmly}{A smooth, dry surface helps the tiles adhere to the wall.}{adhere to the wall}
\vocabentry{302}{conjunction}{n.}{n. 结合，同时发生}{a word such as 'and', 'but', 'while', or ' although ' that connects words, phrases, and clauses in a sentence}{—}{—}
\vocabentry{303}{blend}{v.}{v. 混合}{to mix or combine things together, or to mix or combine with something else, to make one substance}{In a separate bowl, blend the egg and cream.}{blend into the butter}
\vocabentry{304}{hint}{n.}{n. 暗示，示意}{something that you say or do that shows what you think or want, usually in a way that is not direct}{He's dropped (= given) several hints to the boss that he'll quit if he doesn't get a promotion.}{hint to the boss that}
\vocabentry{305}{plausible}{adj.}{adj. 似乎有理的，貌似可信的}{seeming likely to be true, or able to be believed}{a plausible explanation / excuse}{—}
\vocabentry{306}{inventory}{n.}{n. 存货清单；详细目录}{a detailed list of all the things in a place}{A set of 24 gilded chairs appear on the inventory of the house for 1736.}{inventory of the house for}
\vocabentry{307}{pure}{adj.}{adj. 纯粹的}{not mixed with anything else}{a pure cotton shirt}{—}
\vocabentry{308}{counter}{v.}{v. 反驳；抵制}{to react to something with an opposing opinion or action, or to defend yourself against something}{After the government bombed their camp, the rebels countered with an attack on the capital.}{counter with an attack on}
\vocabentry{309}{stale}{adj.}{adj. 走味的}{no longer new or fresh, usually as a result of being kept for too long}{The bread / biscuits / cake had gone stale.}{—}
\vocabentry{310}{virgin}{adj.}{adj. 原始的，未开发的}{A virgin forest or area of land has not yet been cultivated (= used to grow crops) or used by people}{The railway is being extended into areas of virgin forest.}{—}
\vocabentry{311}{catalog}{n.}{n. 目录，目录册，商品目录}{US spelling of catalogue}{—}{—}
\vocabentry{312}{immense}{adj.}{adj. 巨大的，广大的}{extremely large in size or degree}{immense wealth / value}{—}
\vocabentry{313}{intimate}{adj.}{adj. 亲密的，密切的}{having, or being likely to cause, a very close friendship or personal or sexual relationship}{intimate relationships}{intimate with an actress}
\vocabentry{314}{irrespective}{adj.}{adj. 不考虑的，不顾的}{without considering; not needing to allow for}{The payments remain the same, irrespective of any changes in a person's income.}{irrespective of any changes in}
\vocabentry{315}{enforce}{v.}{v. 执行}{to make people obey a law, or to make a particular situation happen or be accepted}{It isn't always easy for the police to enforce speed limits.}{—}
\vocabentry{316}{invert}{v.}{v. 倒置；倒转；颠倒}{to turn something upside down or change the order of two things}{In some languages, the word order in questions is inverted (= the verb comes before the subject of the sentence).}{—}
\vocabentry{317}{punctual}{adj.}{adj. 准时的，守时的}{arriving, doing something, or happening at the expected, correct time; not late}{a punctual start to the meeting}{—}
\vocabentry{318}{ponder}{v.}{v. 仔细考虑，沉思}{to think carefully about something, especially for a noticeable length of time}{She sat back for a minute to ponder her next move in the game.}{—}
\vocabentry{319}{resent}{v.}{v. 愤恨，憎恶}{to feel angry because you have been forced to accept someone or something that you do not like}{She bitterly resented her father's new wife.}{—}
\vocabentry{320}{temper}{n.}{n. 脾气，性情}{the tendency to become angry very quickly}{She has a real temper.}{lose your temper：B2 to suddenly become angry: The children behaved so badly that I lost my temper.； keep your temper：C2 to succeed in staying calm and not becoming angry: I found it hard to keep my temper with so many things going wrong.}
\vocabentry{321}{perception}{n.}{n. 感知；观念，看法}{a belief or opinion, often held by many people and based on how things seem}{We have to change the public's perception that money is being wasted.}{perception that money is being}
\vocabentry{322}{bizarre}{adj.}{adj. 稀奇古怪的}{very strange and unusual}{a bizarre situation}{—}
\vocabentry{323}{trigger}{vt.}{vt. 触发，引起，激发}{to cause something to start}{Some people find that certain foods trigger their headaches.}{trigger off a wave of}
\vocabentry{324}{rigorous}{adj.}{adj. 严厉的，严格的}{careful to look at or consider every part of something to make certain it is correct or safe}{rigorous testing / checking / methods}{—}
\vocabentry{325}{integral}{adj.}{adj. 必需的，必不可少的}{necessary and important as a part of a whole}{He's an integral part of the team and we can't do without him.}{integral to the social life}
\vocabentry{326}{preside}{v.}{v. 主持}{to be in charge of a formal meeting, ceremony, or trial}{Who would be the best person to preside at/over the public enquiry?}{preside over the official enquiry}
\vocabentry{327}{asset}{n.}{n. 财产，资产}{a useful or valuable quality, skill, or person}{He'll be a great asset to the team.}{asset to the team}
\vocabentry{328}{converge}{v.}{v. 汇集，聚集，集中}{If lines, roads, or paths converge, they move towards the same point where they join or meet}{The paths all converge at the main gate of the park.}{converge at the main gate}
\vocabentry{329}{vocational}{adj.}{adj. 职业的；业务的}{(of an educational course or a qualification) providing knowledge and skills that prepare you for a particular job}{The Swedes regard vocational training as a part of a young person's education.}{—}
\vocabentry{330}{resemblance}{n.}{n. 相似}{the fact that two people or things look like each other or are similar in some other way}{There was a clear family resemblance between all the brothers.}{resemblance between all the brothers}
\vocabentry{331}{premium}{n.}{n. 额外费用，溢价}{an amount that is more than usual}{We're willing to pay a premium for the best location.}{premium for the best location}
\vocabentry{332}{prevail}{v.}{v. 流行，普遍存在}{to get control or influence}{I am sure that common sense will prevail in the end.}{prevail in the end}
\vocabentry{333}{divorce}{n.}{n. 离婚，离异； v. 离婚}{an official or legal process to end a marriage}{The last I heard they were getting a divorce.}{—}
\vocabentry{334}{accord}{v.}{v. （与…）一致，符合}{to treat someone specially, usually by showing respect}{The massed crowds of supporters accorded him a hero's welcome.}{accord to doctors and lawyers}
\vocabentry{335}{vulnerable}{adj.}{adj. 易受影响的，易受攻击的；脆弱的}{able to be easily physically or mentally hurt, influenced, or attacked}{I felt very vulnerable, standing there without any clothes on.}{vulnerable to attack, because they}
\vocabentry{336}{concise}{adj.}{adj. 简洁的，简要的；简明的，简略的}{short and clear, expressing what needs to be said without unnecessary words}{Make your answers clear and concise.}{—}
\vocabentry{337}{apprehension}{n.}{n. 忧虑，担心，疑惧}{worry about the future, or a fear that something unpleasant is going to happen}{It's normal to feel a little apprehension before starting a new job.}{apprehension before starting a new}
\vocabentry{338}{toss}{v.}{v. 扔，抛，掷}{to throw something carelessly}{He glanced at the letter and then tossed it into the bin.}{—}
\vocabentry{339}{prescription}{n.}{n. 处方，药方}{a piece of paper or an electronic document on which a doctor writes the details of the medicine or other treatment that someone needs}{a doctor's prescription}{prescription for sedatives}
\vocabentry{340}{anonymous}{adj.}{adj. 匿名的}{made or done by someone whose name is not known or not made public}{The money was donated by an anonymous benefactor.}{—}
\vocabentry{341}{attribute}{v.}{v. 把……归因于，把……归咎于}{to say or think that something is the result of a particular thing}{Her success can be attributed to three main factors.}{attribute to three main factors}
\vocabentry{342}{swarm}{n.}{n. 一群，一批人}{a large group of insects all moving together}{a swarm of bees / wasps / ants / locusts}{swarm of bees / wasps}
\vocabentry{343}{bleak}{adj.}{adj. 无希望的}{If a place is bleak, it is empty, and not welcoming or attractive}{The house stands on a bleak, windswept hilltop.}{—}
\vocabentry{344}{dedicate}{v.}{v. 献给（把书籍、戏剧、演出等）}{to give all of your energy, time, etc.}{He has dedicated his life to scientific research.}{dedicate oneself to protecting the rights}
\vocabentry{345}{timid}{adj.}{adj. 腼腆的}{shy and nervous; without much confidence; easily frightened}{Kieran is a timid child.}{—}
\vocabentry{346}{occasional}{adj.}{adj. 偶尔的}{not happening or done often or regularly}{I play the occasional game of tennis.}{—}
\vocabentry{347}{chord}{n.}{n. 和弦}{three or more musical notes played at the same time}{She strummed a few chords on her guitar.}{chord on her guitar}
\vocabentry{348}{sector}{n.}{n. （经济等的）行业；部门}{one of the areas into which the economic activity of a country is divided}{In the financial sector, banks and insurance companies have both lost a lot of money.}{sector to the private sector}
\vocabentry{349}{remnant}{n.}{n. 遗迹}{a small piece or amount of something that is left from a larger original piece or amount}{the remnants of last night's meal}{remnant of last night's meal}
\vocabentry{350}{commend}{v.}{v. 称赞}{to formally praise someone or something}{The judge commended her for her bravery.}{—}
\vocabentry{351}{permeate}{v.}{v. 渗透}{to spread through something and be present in every part of it}{Dissatisfaction with the government seems to have permeated every section of society.}{permeate into the wood beneath}
\vocabentry{352}{gross}{adj.}{adj. 总的，毛重的}{(in) total}{A person's gross income is the money they earn before tax is deducted from it.}{—}
\vocabentry{353}{transient}{adj.}{adj. 短暂的；转瞬即逝的；n. 过客}{lasting for only a short time; temporary}{A glass of whisky has only a transient warming effect.}{—}
\vocabentry{354}{ambiguous}{adj.}{adj. 含糊不清的}{having or expressing more than one possible meaning, sometimes intentionally}{His reply to my question was somewhat ambiguous.}{ambiguous on this issue}
\vocabentry{355}{commute}{n.}{n. 通勤，在两地之间乘车往返}{a regular journey between work and home}{It's at least an hour's commute to work.}{commute to work}
\vocabentry{356}{articulate}{v.}{v. 明确表达}{to express in words}{I found myself unable to articulate my feelings.}{—}
\vocabentry{357}{adverse}{adj.}{adj. 不利的}{having a negative or harmful effect on something}{They received a lot of adverse publicity about the changes.}{—}
\vocabentry{358}{blunder}{n.}{n. 愚蠢之举；大错； v. 犯大错；失策；绊倒}{a serious mistake, usually caused by not taking care or thinking}{He said that the tax was a major political blunder.}{blunder by getting his name}
\vocabentry{359}{facet}{n.}{n. （事物的）部分，方面}{one part of a subject, situation, etc. that has many parts}{She has so many facets to her personality.}{facet to her personality}
\vocabentry{360}{stubborn}{adj.}{adj. 顽固的；倔强的}{A stubborn person is determined to do what he or she wants and refuses to do anything else}{They have huge arguments because they're both so stubborn.}{—}
\vocabentry{361}{reinforce}{v.}{v. 加强}{to make something stronger}{The pockets on my jeans are reinforced with double stitching.}{reinforce with double stitching}
\vocabentry{362}{comb}{v.}{v. 梳（头发）}{to tidy your hair using a comb}{She combed her hair and put on some lipstick.}{comb out (= remove using}
\vocabentry{363}{smuggle}{v.}{v. 走私}{to take things or people to or from a place secretly and often illegally}{She was caught trying to smuggle 26 kilos of heroin out of/into the country.}{—}
\vocabentry{364}{dwell}{v.}{v. （尤指作为常住居民）居住}{to live in a place or in a particular way}{She dwelt in remote parts of Asia for many years.}{—}
\vocabentry{365}{hook}{v.}{v. 对……入了迷}{to fasten something with a hook, hang something on a hook, or catch something with a hook}{He hooked the trailer (= joined it with a hook) to his car.}{—}
\vocabentry{366}{colony}{n.}{n. 群体；菌落}{a country or area controlled politically by a more powerful country that is often far away}{Australia and New Zealand are former British colonies.}{—}
\vocabentry{367}{undermine}{vt.}{vt. 暗中破坏；逐渐削弱；侵蚀……的基础}{to make someone less confident, less powerful, or less likely to succeed, or to make something weaker, often gradually}{The president has accused two cabinet members of working secretly to undermine his position /him.}{—}
\vocabentry{368}{hinder}{v.}{v. 阻碍，妨碍}{to limit the ability of someone to do something, or to limit the development of something}{High winds have hindered firefighters in their efforts to put out the blaze.}{hinder by her lack of}
\vocabentry{369}{sophisticated}{adj.}{adj. 精密的；老练的}{having a good understanding of the way people behave and/or a good knowledge of culture and fashion}{She was slim, svelte, and sophisticated.}{—}
\vocabentry{370}{trait}{n.}{n. 特征}{a particular characteristic that can produce a particular type of behaviour}{His sense of humour is one of his better traits.}{—}
\vocabentry{371}{merit}{n.}{n. 优点；价值}{the quality of being good and deserving praise}{an entertaining film with little artistic merit}{the merits of something：the advantages something has compared to something else: We discussed the merits of herbal tea.； on someone's/something's merits (also on someone's/something's own merits, on someone's/something's own merit, on someone's/something's merit)：according to the qualities that someone or something has or has shown, without considering any other information or comparing them to someone or something else: The committee will consider each applicant on his or her own merits.}
\vocabentry{372}{notwithstanding}{prep.}{prep. 尽管，虽然； adv.尽管，虽然}{despite the fact or thing mentioned}{Notwithstanding some members ' objections, I think we must go ahead with the plan.}{—}
\vocabentry{373}{liquor}{n.}{n. 酒}{strong alcoholic drink}{He spent most of his money on liquor and drugs.}{—}
\vocabentry{374}{prey}{n.}{n. 猎物}{an animal that is hunted and killed for food by another animal}{A hawk hovered in the air before swooping on its prey.}{—}
\vocabentry{375}{inaugurate}{v.}{v. 为……揭幕；为……举行就职典礼；开展，投入使用}{to put someone into an official position with a ceremony}{American presidents are always inaugurated on 20 January.}{inaugurate on 20 January}
\vocabentry{376}{disguise}{v.}{v. 掩饰，掩盖}{to give a new appearance to a person or thing, especially in order to hide its true form}{He disguised himself by wearing a false beard.}{disguise oneself by wearing a false}
\vocabentry{377}{deposit}{n.}{n. 沉积物，矿藏}{a substance or layer that is left, usually after a liquid is removed}{Decant the wine carefully, so that you leave the deposit in the bottom of the bottle.}{deposit in the bottom of}
\vocabentry{378}{vex}{v.}{v. 使烦恼，使苦恼，使恼怒}{to cause difficulty to someone, or to cause someone to feel angry, annoyed, or upset}{This issue looks likely to continue to vex the government.}{—}
\vocabentry{379}{reckon}{vt.}{vt. 估算；认为}{to think or believe}{I reckon it's going to rain.}{—}
\vocabentry{380}{suppress}{v.}{v. 抑制（感情等）}{to end something by force}{The Hungarian uprising in 1956 was suppressed by the Soviet Union.}{suppress by the Soviet Union}
\vocabentry{381}{betray}{v.}{v. 泄露（秘密等）}{to not be loyal to your country or a person, often by doing something harmful such as helping their enemies}{He was accused of betraying his country during the war.}{betray by her mother's lack}
\vocabentry{382}{imperative}{adj.}{adj. 必要的}{extremely important or urgent}{The president said it was imperative that the release of all hostages be secured.}{imperative that the release of}
\vocabentry{383}{doctrine}{n.}{n. 教条，学说，信条，原则}{a belief or set of beliefs, especially political or religious ones, that are taught and accepted by a particular group}{Christian doctrine}{—}
\vocabentry{384}{undertaking}{n.}{n. 任务}{a job, business, or piece of work}{The construction of the tunnel is a large and complex undertaking.}{—}
\vocabentry{385}{subsidy}{n.}{n. 补助金，津贴}{money given as part of the cost of something, to help or encourage it to happen}{The company received a substantial government subsidy.}{—}
\vocabentry{386}{garment}{n.}{n. 服装}{a piece of clothing}{—}{—}
\vocabentry{387}{spectrum}{n.}{n. 光谱；范围}{the set of colours into which a beam of light can be separated, or a range of waves, such as light waves or radio waves}{The colours of the spectrum - red, orange, yellow, green, blue, indigo, and violet - can be seen in a rainbow.}{—}
\vocabentry{388}{nominate}{v.}{v. 提名；任命}{to officially suggest someone for an election, job, position, or honour}{He's been nominated by the Green Party as their candidate in the next election.}{nominate by the Green Party}
\vocabentry{389}{hazard}{n.}{n. 危险}{something that is dangerous and likely to cause damage}{a health / fire hazard}{hazard to pedestrians}
\vocabentry{390}{repent}{v.}{v. 后悔}{to be very sorry for something bad you have done in the past and wish that you had not done it}{He repented (of his sins) just hours before he died.}{—}
\vocabentry{391}{incentive}{n.}{n. 刺激，激励}{something that encourages a person to do something by offering them a reward}{Bonus payments provide an incentive to work harder.}{incentive to work harder}
\vocabentry{392}{precaution}{n.}{n. 预防措施}{an action that is done to prevent something unpleasant or dangerous happening}{Many people have been stockpiling food as a precaution against shortages.}{precautions [ plural ]：a polite way of referring to contraception (= methods that prevent a woman becoming pregnant): If you're going to have sex, make sure you take precautions.}
\vocabentry{393}{superficial}{adj.}{adj. 肤浅的}{(of a person) never thinking about things that are serious or important}{He's fun to be with, but he's very superficial.}{—}
\vocabentry{394}{scout}{v.}{v. 侦察}{to go to look in various places for something you want}{He's scouting about/around for somewhere better to live.}{scout out (= discover information}
\vocabentry{395}{perpetual}{adj.}{adj. 永远的，永恒的}{continuing for ever in the same way}{They lived in perpetual fear of being discovered.}{—}
\vocabentry{396}{solemn}{adj.}{adj. 严肃的；庄严的，隆重的}{serious and without any humour}{a solemn face / voice}{solemn promise, commitment, undertaking, etc.：an agreement that you make in a serious way and expect to keep: I'd made a solemn promise and I was determined to keep it.}
\vocabentry{397}{violate}{v.}{v. 违反，违背；侵犯，妨碍}{to break or act against something, especially a law, agreement, principle, or something that should be treated with respect}{They were charged with violating federal law.}{—}
\vocabentry{398}{stripe}{n.}{n. 类型，类别}{a strip on the surface of something that is a different colour from the surrounding surface}{The zebra is a wild African horse with black and white stripes.}{—}
\vocabentry{399}{tedious}{adj.}{adj. 沉闷的，冗长乏味的}{boring}{a tedious job}{—}
\vocabentry{400}{augment}{v.}{v. 增加；助长}{to increase the size or value of something by adding something to it}{He would have to find work to augment his income.}{—}
\vocabentry{401}{wit}{n.}{n. 智力，才智；机智}{the ability to use words in a clever and humorous way}{a woman of great intelligence and wit}{—}
\vocabentry{402}{dull}{adj.}{adj. 枯燥的，沉闷的}{not interesting or exciting in any way}{She wrote dull, respectable articles for the local newspaper.}{—}
\vocabentry{403}{ignorance}{n.}{n. 无知}{lack of knowledge, understanding, or information about something}{Public ignorance about the disease is still a cause for concern.}{ignorance about the disease is}
\vocabentry{404}{badge}{n.}{n. 徽章}{a small piece of metal or plastic with words or a picture on it, that you carry with you or fasten to your clothing or something else, in order to show who you are, that you are a member of a group, etc.}{Everyone at the conference wore a badge with their name on.}{badge with their name on}
\vocabentry{405}{terminate}{vt.}{vt. 使结束，终止}{to (cause something to) end or stop}{They terminated my contract in October.}{terminate at the next stop}
\vocabentry{406}{lubricate}{v.}{v. 使……润滑；给……加润滑油}{to use a substance such as oil to make a machine or device operate more easily, or to prevent something sticking or rubbing}{A car engine needs to be well lubricated with oil.}{lubricate with oil}
\vocabentry{407}{assure}{vt.}{vt. 向……保证，使确信}{to tell someone confidently that something is true, especially so that they do not worry}{The unions assured the new owners of the workers ' loyalty to the company.}{—}
\vocabentry{408}{degrade}{v.}{v. 贬低；降低品格（身价、价值等）}{to cause people to feel that they or other people have no value and do not have the respect or good opinion of others}{Pornography degrades women.}{degrade oneself by begging for something}
\vocabentry{409}{significance}{n.}{n. 意义，含义}{importance}{The discovery of the new drug is of great significance for/to people suffering from heart problems.}{—}
\vocabentry{410}{fling}{v.}{v. 掷，抛；猛烈地移动；n. 尽情欢乐的一阵，一时}{to throw something or someone suddenly and with a lot of force}{He crumpled up the letter and flung it into the fire.}{—}
\vocabentry{411}{intricate}{adj.}{adj. 错综复杂的；复杂精细的}{having a lot of small parts that are arranged in a complicated or delicate way}{The watch mechanism is extremely intricate and very difficult to repair.}{—}
\vocabentry{412}{prescribe}{vt.}{vt. 给……开药}{(of a doctor) to say what medical treatment someone should have}{The drug is often prescribed for ulcers.}{prescribe for ulcers}
\vocabentry{413}{auxiliary}{adj.}{adj. 备用的，辅助的，协助的}{giving help or support, especially to a more important person or thing}{auxiliary staff / nurses}{—}
\vocabentry{414}{reconcile}{v.}{v. 调解}{to find a way in which two situations or beliefs that are opposed to each other can agree and exist together}{It is sometimes difficult to reconcile science and religion.}{be reconciled：When two people are reconciled, they become friendly again after they have argued: be reconciled with They were finally reconciled with each other, after not speaking for nearly five years.}
\vocabentry{415}{momentum}{n.}{n. （物理）动量；势头；动力}{the property of a moving object that makes it continue travelling at the same speed and in the same direction unless another object or force affects its movement}{Once you push it, it keeps going under its own momentum.}{momentum for its trip to}
\vocabentry{416}{commonwealth}{n.}{n. 联邦}{a group of countries with the same political or economic aims}{Thomas Hobbes claimed that in a state of nature, people constantly fight against each other, and that the only way to overcome this is to form a commonwealth.}{commonwealth of Independent States (CIS)was}
\vocabentry{417}{negligible}{adj.}{adj. 微不足道的，可忽略不计的}{too slight or small in amount to be of importance}{The difference between the two products is negligible.}{—}
\vocabentry{418}{deceit}{n.}{n. 欺骗，欺诈}{(an act of) keeping the truth hidden, especially to get an advantage}{The story is about theft, fraud, and deceit on an incredible scale.}{deceit on an incredible scale}
\vocabentry{419}{contrive}{v.}{v. 设计，发明；设计出；设法做到；谋划，策划}{to arrange a situation or event, or arrange for something to happen, using clever planning}{Couldn't you contrive a meeting between them? I think they'd really like each other.}{contrive to get tickets for}
\vocabentry{420}{pendulum}{n.}{n. 摆，钟摆；摇摆不定的事态（或局面）}{a device consisting of a weight on a stick or thread that moves from one side to the other, especially one that forms a part of some types of clocks}{The pendulum in the grandfather clock swung back and forth.}{pendulum in the grandfather clock}
\vocabentry{421}{sensible}{adj.}{adj. 明智的，理智的}{based on or acting on good judgment and practical ideas or understanding}{a sensible answer / approach / compromise / option}{sensible to take an umbrella}
\vocabentry{422}{retain}{v.}{v. 保持，保留，保存}{to keep or continue to have something}{She has lost her battle to retain control of the company.}{—}
\vocabentry{423}{commemorate}{v.}{v. 纪念，庆祝}{to remember officially and give respect to a great person or event, especially by a public ceremony or by making a statue or special building}{Gathered all together in this church, we commemorate those who lost their lives in the war.}{—}
\vocabentry{424}{mute}{adj.}{adj. 无声的，宁静的}{silent or not speaking}{The president has remained mute about plans to curtail the number of immigrants.}{mute about plans to curtail}
\vocabentry{425}{allocate}{v.}{v. 分配，配给}{to give something to someone as their share of a total amount, to use in a particular way}{The government is allocating £10 million for health education.}{—}
\vocabentry{426}{overthrow}{v.}{v. 推翻，使终止，摒弃}{to defeat or remove someone from power, using force}{He said that Allende's government in Chile was overthrown by the army and the CIA in 1973.}{—}
\vocabentry{427}{compulsory}{adj.}{adj. 必修的}{If something is compulsory, you must do it because of a rule or law}{Swimming was compulsory at my school.}{compulsory at my school}
\vocabentry{428}{headquarters}{n.}{n. 总部，总局}{the main offices of an organization such as the army, the police, or a business company}{The company's headquarters is/are in Amsterdam.}{—}
\vocabentry{429}{acquaintance}{n.}{n. 相识的人，熟人}{a person that you have met but do not know well}{a business acquaintance}{—}
\vocabentry{430}{friction}{n.}{n. 摩擦，摩擦力}{the force that makes it difficult for one object to slide along the surface of another or to move through a liquid or gas}{When you rub your hands together the friction produces heat.}{—}
\vocabentry{431}{ensue}{v.}{v. 跟着发生，接踵而来}{to happen after something else, especially as a result of it}{The police officer said that he had placed the man under arrest and that a scuffle had ensued.}{—}
\vocabentry{432}{entity}{n.}{n. 实体，存在}{something that exists apart from other things, having its own independent existence}{The museums work closely together, but are separate legal entities.}{—}
\vocabentry{433}{feeble}{adj.}{adj. 虚弱的}{weak and without energy, strength, or power}{He was a feeble, helpless old man.}{—}
\vocabentry{434}{hover}{v.}{v. 徘徊}{to stay in one place in the air, usually by moving the wings quickly}{A hawk hovered in the sky, waiting to swoop down on its prey.}{hover in the sky, waiting}
\vocabentry{435}{distort}{v.}{v. 扭曲，使变形}{to change the shape of something so that it looks strange or unnatural}{The map distorted Greenland to appear four times its actual size.}{—}
\vocabentry{436}{scarce}{adj.}{adj. 缺乏的，不足的}{not easy to find or get}{Food and clean water were becoming scarce.}{—}
\vocabentry{437}{agitation}{n.}{n. 焦虑，忧虑；摇动}{worry and anxiety}{He arrived home in a state of agitation.}{—}
\vocabentry{438}{relatively}{adv.}{adv. 比较地，相对地}{quite good, bad, etc. in comparison with other similar things or with what you expect}{He's a relatively good squash player.}{relatively good, bad, etc.：B2 quite good, bad, etc. in comparison with other similar things or with what you expect: He's a relatively good squash player. There was relatively little violence. More examples Fewer examples These people are living on relatively low incomes. It is relatively easy for newcomers to pick off the most lucrative business and ignore the rest. These beautiful old towns have remained relatively untouched by tourism. The third candidate for the party leadership is a relatively unknown quantity. The country's great influence in the world is disproportionate to its relatively small size.； relatively speaking：said when you are judging one thing in comparison with other things: Relatively speaking, it's a fairly poor country.}
\vocabentry{439}{muddy}{v.}{v. 搅乱}{to put mud (= wet, sticky earth) into something or cover something with mud}{Industrial activity has muddied the river.}{—}
\vocabentry{440}{federal}{adj.}{adj. 联邦政府的}{relating to the central government, and not to the government of a region, of some countries such as the US}{the federal government}{—}
\vocabentry{441}{rehearsal}{n.}{n. 排练，排演}{a time when all the people involved in a play, dance, etc. practise in order to prepare for a performance}{They didn't have time for (a) rehearsal before the performance.}{rehearsal before the performance}
\vocabentry{442}{confront}{vt.}{vt. 面对；正视；与……对抗}{to face, meet, or deal with a difficult situation or person}{As she left the court, she was confronted by angry crowds who tried to block her way.}{confront by angry crowds who}
\vocabentry{443}{Canon}{n.}{n. 标准，教规，正典圣经，教士}{a Christian priest with special duties in a cathedral}{—}{—}
\vocabentry{444}{farewell}{n.}{n. 再见}{an occasion when someone says goodbye}{We said our sad farewells and got on the bus.}{farewell to the star}
\vocabentry{445}{fortnight}{n.}{n. 两星期}{a period of two weeks}{a fortnight's holiday}{—}
\vocabentry{446}{dubious}{adj.}{adj. 怀疑的；可疑的；无把握的}{thought not to be completely true or not able to be trusted}{These claims are dubious and not scientifically proven.}{—}
\vocabentry{447}{deem}{v.}{v. 认为，视为}{to consider or judge something in a particular way}{The area has now been deemed safe.}{deem to have withdrawn from}
\vocabentry{448}{precede}{v.}{v. 发生在……之前，先于}{to be or go before something or someone in time or space}{Kofi Annan preceded Ban Ki-moon as the Secretary-General of the UN.}{—}
\vocabentry{449}{cripple}{n.}{n. 跛子，不健全的人； v.严重削弱；使跛}{an extremely offensive word for a person whose legs or arms do not work in the usual way}{—}{emotional cripple offensive：an offensive phrase for someone who finds it difficult to have or express feelings}
\vocabentry{450}{stem}{v.}{v. 起源于； n. 茎，（树）干}{to stop something unwanted from spreading or increasing}{These measures are designed to stem the rise of violent crime.}{—}
\vocabentry{451}{exceedingly}{adv.}{adv. 过分地}{to a very great degree}{He was clever, handsome, and exceedingly rich.}{—}
\vocabentry{452}{feasible}{adj.}{adj. 可行的，行得通的}{able to be made, done, or achieved}{With the extra resources, the project now seems feasible.}{feasible to clone human beings,}
\vocabentry{453}{principal}{adj.}{adj. 主要的，首要的}{first in order of importance}{Iraq's principal export is oil.}{—}
\vocabentry{454}{intermittent}{adj.}{adj. 断断续续的，间歇的}{not happening regularly or continuously; stopping and starting repeatedly or with periods in between}{intermittent rain}{—}
\vocabentry{455}{indignation}{n.}{n. 愤慨}{anger about a situation that you think is wrong or not fair}{—}{—}
\vocabentry{456}{consent}{n.}{n. 同意，准许；赞成； v.同意}{permission or agreement}{They can't publish your name without your consent.}{by common consent mainly UK：most people agree: Her latest novel, by common consent, is her best yet.}
\vocabentry{457}{appreciable}{adj.}{adj. 可察觉的}{If an amount or change is appreciable, it is large or noticeable enough to have an important effect}{There has been an appreciable drop in the number of unemployed since the new government came to power.}{—}
\vocabentry{458}{compatible}{adj.}{adj. 合得来的}{able to exist, live, or work successfully with something or someone else}{It was when we started living together that we found we just weren't compatible.}{compatible with democratic government}
\vocabentry{459}{deduce}{v.}{v. 推论，推断；演绎}{to reach an answer or a decision by thinking carefully about the known facts}{We cannot deduce very much from these figures.}{deduce that he must have}
\vocabentry{460}{grant}{v.}{v. （勉强）承认；授予，给予}{to give or allow someone something, usually in an official way}{They granted her an entry visa.}{—}
\vocabentry{461}{margin}{n.}{n. 利润}{the amount by which one thing is different from another}{The Senate approved the use of military force by a margin of 52 votes to 47.}{margin of 52 votes to}
\vocabentry{462}{unanimous}{adj.}{adj. 一致同意的；全体一致的}{If a group of people are unanimous, they all agree about one particular matter or vote the same way, and if a decision or judgment is unanimous, it is formed or supported by everyone in a group}{The jury returned a unanimous verdict of guilty after a short deliberation.}{—}
\vocabentry{463}{liberal}{adj.}{adj. 人文（教育）的}{respecting and allowing many different types of beliefs or behaviour}{a liberal society / attitude}{—}
\vocabentry{464}{dump}{vt.}{vt. 倾销，抛售； n. 垃圾场，废物堆}{to put down or drop something in a careless way}{He came in with four shopping bags and dumped them on the table.}{—}
\vocabentry{465}{rectify}{v.}{v. 纠正}{to correct something or make something right}{I am determined to take whatever action is necessary to rectify the situation.}{—}
\vocabentry{466}{confine}{v.}{v. 限制}{to limit an activity, person, or problem in some way}{Let's confine our discussion to the matter in question, please!}{be confined to somewhere/something：to exist only in a particular area or group of people: We know that the illness is not confined to any one group in society.}
\vocabentry{467}{reap}{v.}{v. 获得}{to cut and collect a grain crop}{The serfs had to cultivate the lord's land, to make his hay, and reap and gather in his harvest.}{—}
\vocabentry{468}{clash}{vi.}{vi. 发生冲突}{to fight or argue}{Students clashed with police after demonstrations at five universities.}{clash with police after demonstrations}
\vocabentry{469}{spectacle}{n.}{n. 景象，奇观}{an unusual or unexpected event or situation that attracts attention, interest, or disapproval}{It was a strange spectacle to see the two former enemies shaking hands and slapping each other on the back.}{spectacle to see the two}
\vocabentry{470}{scarcely}{adv.}{adv. 几乎不}{almost not}{I was scarcely able to move my arm after the accident.}{—}
\vocabentry{471}{perplex}{v.}{v. 使困惑}{to confuse and worry someone slightly by being difficult to understand or solve}{The disease has continued to perplex doctors.}{—}
\vocabentry{472}{transparent}{adj.}{adj. 显而易见的；透明的，清澈的}{If a substance or object is transparent, you can see through it very clearly}{Grow the bulbs in a transparent plastic box, so the children can see the roots growing.}{—}
\vocabentry{473}{hamper}{v.}{v. 阻碍，妨碍，牵制}{to prevent someone doing something easily}{Fierce storms have been hampering rescue efforts and there is now little chance of finding more survivors.}{—}
\vocabentry{474}{bind}{v.}{v. 捆绑；装订；约束；结合}{to tie something or someone tightly or to fasten something}{They bound the packages with brightly coloured ribbon.}{—}
\vocabentry{475}{contemplate}{v.}{v. 注视}{to spend time considering a possible future action, or to consider one particular thing for a long time in a serious and quiet way}{I'm contemplating go ing abroad for a year.}{—}
\vocabentry{476}{stereotype}{n.}{n. 老套的模式，陈规； v.对……产生成见}{a set idea that people have about what someone or something is like, especially an idea that is wrong}{racial / sexual stereotypes}{stereotype of a Frenchman}
\vocabentry{477}{inertia}{n.}{n. 惰性}{lack of activity or interest, or unwillingness to make an effort to do anything}{The organization is stifled by bureaucratic inertia.}{—}
\vocabentry{478}{arrogant}{adj.}{adj. 傲慢的，妄自尊大的}{unpleasantly proud and behaving as if you are more important than, or know more than, other people}{I found him arrogant and rude.}{—}
\vocabentry{479}{solitude}{n.}{n. 独处，独居}{the situation of being alone without other people}{a life of solitude}{solitude at sea it felt}
\vocabentry{480}{hectic}{adj.}{adj. 紧张的，忙碌的}{full of activity, or very busy and fast}{a hectic schedule}{—}
\vocabentry{481}{emancipate}{v.}{v. 解放}{to give people social or political freedom and rights}{—}{—}
\vocabentry{482}{endorse}{v.}{v. 赞同，认可}{to make a public statement of your approval or support for something or someone}{The Council is expected to endorse the committee's recommendations.}{—}
\vocabentry{483}{negligent}{adj.}{adj. 疏忽的，粗心大意的}{not being careful or giving enough attention to people or things that are your responsibility}{The judge said that the teacher had been negligent in allow ing the children to swim in dangerous water.}{negligent in allow ing the}
\vocabentry{484}{evade}{v.}{v. 躲避，回避}{to avoid or escape from someone or something}{The police have assured the public that the escaped prisoners will not evade recapture for long.}{evade the issue, question, etc.：to intentionally not talk about something or not answer something: Just give me an answer and stop evading the question!}
\vocabentry{485}{complexion}{n.}{n. 肤色}{the natural appearance of the skin on a person's face, especially its colour or quality}{—}{—}
\vocabentry{486}{obsess}{vt.}{vt. 迷住，使着迷，使烦扰}{If something or someone obsesses you, or if you obsess about something or someone, you think about it, him, or her all the time}{The whole relationship obsessed me for years.}{obsess about her weight}
\vocabentry{487}{devastate}{v.}{v. 摧毁}{to destroy a place or thing completely or cause great damage}{—}{—}
\vocabentry{488}{prestigious}{adj.}{adj. 有名望的，有威信的}{very much respected and admired, usually because of being important}{a prestigious literary award}{—}
\vocabentry{489}{atrocity}{n.}{n. 残暴，暴行}{an extremely cruel, violent, or shocking act}{They are on trial for committing atrocities against the civilian population.}{—}
\vocabentry{490}{morale}{n.}{n. 士气，斗志}{the amount of confidence felt by a person or group of people, especially when in a dangerous or difficult situation}{A couple of victories would improve the team's morale enormously.}{—}
\vocabentry{491}{oppression}{n.}{n. 压迫}{a situation in which people are governed in an unfair and cruel way and prevented from having opportunities and freedom}{Every human being has the right to freedom from oppression.}{oppression of women}
\vocabentry{492}{decree}{v.}{v. 命令，判决，颁布}{to officially decide or order that something must happen}{They decreed an end to discrimination on grounds of age.}{decree that all new buildings}
\vocabentry{493}{hybrid}{adj.}{adj. 混合的}{combining two different things}{His choreography is described as "a hybrid mix of mime and circus tricks ".}{—}
\vocabentry{494}{retarded}{adj.}{adj. 智力迟钝的}{a word used to describe a person with a learning disability (= a condition that can have an effect on someone's ability to learn easily), which was used by doctors in the past but is now extremely offensive}{—}{—}
\vocabentry{495}{allure}{n.}{n. 诱惑力，吸引力}{the quality of being attractive, interesting, or exciting}{the allure of work ing in television}{allure of work ing in}
\vocabentry{496}{frantic}{adj.}{adj. 紧张忙乱的，手忙脚乱的}{almost out of control because of extreme emotion, such as worry}{Where on earth have you been? We've been frantic with worry.}{frantic with worry}
\vocabentry{497}{console}{v.}{v. 安慰，慰问}{to make someone who is sad or disappointed feel better, usually by giving them comfort or sympathy}{Her friends tried to console her, telling her "Everything will be fine."}{console by the fact that}
\vocabentry{498}{solicit}{v.}{v. 乞求，恳求给予（帮助或金钱）}{to ask someone for money, information, or help}{to solicit donations for a charity}{—}
\vocabentry{499}{turmoil}{n.}{n. 骚动，混乱}{a state of confusion, uncertainty, or disorder}{The whole region is in turmoil.}{—}
\vocabentry{500}{mint}{v.}{v. 铸造（硬币）}{to produce a coin for the government}{—}{—}
\vocabentry{501}{epidemic}{n.}{n. （犯罪，疾病等的）盛行，流行}{the appearance of a particular disease in a large number of people at the same time}{a flu epidemic}{—}
\vocabentry{502}{counterfeit}{v.}{v. 伪造，仿造； n. 仿制品，伪造物}{to make something look like the original of something else, usually for dishonest or illegal purposes}{Two women and a man have been convicted of counterfeiting \$100 bills.}{—}
\vocabentry{503}{mandatory}{adj.}{adj. 命令的，强制性的}{Something that is mandatory must be done, or is demanded by law}{The minister is calling for mandatory prison sentences for people who assault police officers.}{mandatory to wear rear seat}
\vocabentry{504}{ordeal}{n.}{n. 严峻的考验，苦难的经历，折磨}{a very unpleasant and painful or difficult experience}{The hostages ' ordeal came to an end when soldiers stormed the building.}{—}
\vocabentry{505}{cardinal}{adj.}{adj. 基本的}{of great importance}{—}{—}
\vocabentry{506}{brew}{v.}{v. （风暴、危机等）酝酿，即将来临}{to make beer}{—}{—}
\vocabentry{507}{waive}{v.}{v. 放弃}{to not demand something you have a right to, or not cause a rule to be obeyed}{The bank manager waived the charge (= said we didn't have to pay), as we were old and valued customers.}{—}
\vocabentry{508}{infrastructure}{n.}{n. 基础设施}{the basic systems and services, such as transport and power supplies, that a country or organization uses in order to work effectively}{The war has badly damaged the country's infrastructure.}{—}
\vocabentry{509}{corporal}{adj.}{adj. 身体的； n. (陆军或空军)下士}{of or relating to the body}{At a recent board meeting, policymakers voted to ban corporal punishment.}{—}
\vocabentry{510}{stigma}{n.}{n. 耻辱，污名}{a strong feeling of disapproval that most people in a society have about something, especially when this is unfair}{There is no longer any stigma to being divorced.}{stigma to being divorced}
\vocabentry{511}{erode}{v.}{v. 损害}{to rub or be rubbed away gradually}{Wind and rain have eroded the statues into shapeless lumps of stone.}{—}
\vocabentry{512}{havoc}{n.}{n. 破坏，灾害}{confusion and lack of order, especially causing damage or trouble}{The storm wreaked (= caused) havoc in the garden, uprooting trees and blowing a fence down.}{havoc in the garden, uprooting}
\vocabentry{513}{repress}{vt.}{vt. 抑制}{to not allow something, especially feelings, to be expressed}{He repressed a sudden desire to cry.}{—}
\vocabentry{514}{relentless}{adj.}{adj. 持续的}{continuing in a severe or extreme way}{relentless criticism / pressure}{—}
\vocabentry{515}{deter}{v.}{v. 防止，阻止；使踌躇}{to prevent someone from doing something or to make someone less enthusiastic about doing something by making it difficult for that person to do it or by threatening bad results if they do it}{These measures are designed to deter an enemy attack.}{—}
\vocabentry{516}{feasibility}{n.}{n. 可行性，可能性，现实性}{the possibility that something can be made, done, or achieved, or is reasonable}{We're looking at the feasibility of building a shopping centre there.}{feasibility of building a shopping}
\vocabentry{517}{eradicate}{v.}{v. 根除}{to get rid of something completely or destroy something bad}{The government claims to be doing all it can to eradicate corruption.}{—}
\vocabentry{518}{tactic}{n.}{n. 手段，策略}{a planned way of doing something}{These bomb attacks represent a change of tactics by the terrorists.}{tactics [ plural ]：the organization and use of soldiers and equipment in war: We should leave it to the military men to organize the tactics.}
\vocabentry{519}{benign}{adj.}{adj. 无害的}{pleasant and kind}{a benign old lady}{—}
\vocabentry{520}{crumble}{v.}{v. 崩塌，坍塌}{to break, or cause something to break, into small pieces}{She nervously crumbled the bread between her fingers.}{—}
\vocabentry{521}{avenge}{v.}{v. 报复，报仇；为…雪耻，替…报仇}{to do harm to or punish the person responsible for something bad done to you or your family or friends in order to achieve a fair situation}{He swore he would avenge his brother's death.}{—}
\vocabentry{522}{stipulate}{v.}{v. 规定，明确要求}{to say exactly how something must be or must be done}{She agreed to buy the car, but stipulated racing tyres and a turbo-powered engine.}{stipulate that new cars must}
\vocabentry{523}{leverage}{v.}{v. 利用}{to use something that you already have in order to achieve something new or better}{We can gain a market advantage by leveraging our network of partners.}{—}
\vocabentry{524}{unveil}{vt.}{vt. 揭开，公布}{to remove a covering like a curtain from a new structure at a formal ceremony in order to show the opening or finishing of a new building or work of art}{The memorial to those who had died in the war was unveiled by the Queen.}{unveil by the Queen}
\vocabentry{525}{snob}{n.}{n. 势利小人}{a person who respects and likes only people who are of a high social class, and/or a person who has extremely high standards who is not satisfied by the things that ordinary people like}{He's a terrible snob - if you haven't been to the right school he probably won't even speak to you.}{—}
\vocabentry{526}{imminent}{adj.}{adj. 迫近的，紧迫的，即将来临的}{coming or likely to happen very soon}{imminent disaster / danger}{—}
\vocabentry{527}{dividend}{n.}{n. （股份的）红利，回报，效益}{(a part of) the profit of a company that is paid to the people who own shares in it}{Dividends will be sent to shareholders.}{—}
\vocabentry{528}{toil}{v.}{v. 苦干}{to work hard}{Farm workers have been toiling in the 100-degree heat over the past week.}{toil in the 100-degree heat}
\vocabentry{529}{antonym}{n.}{n. 反义词}{a word that means the opposite of another word}{Two antonyms of " light " are " dark " and " heavy ".}{antonym of " light "}
\vocabentry{530}{onset}{n.}{n. （尤指某种坏事情的）开始}{the moment at which something begins, and especially something uncomfortable or unpleasant}{the onset of winter}{the onset of something：the moment at which something begins, and especially something uncomfortable or unpleasant: the onset of winter}
\vocabentry{531}{warranty}{n.}{n. 保修单}{a written promise from a company to repair or replace a product that develops a fault within a particular period of time, or to do a piece of work again if it is not satisfactory}{The warranty covers the car mechanically for a year, with unlimited mileage.}{—}
\vocabentry{532}{acclaim}{vt.}{vt. 欢呼，喝彩； n. 欢呼，赞扬，称赞}{to give public approval and praise}{She was widely acclaimed for her contribution to the discovery.}{acclaim for her contribution to}
\vocabentry{533}{peg}{v.}{v. 确定，敲定}{to fasten something in place with pegs}{Make sure the tarpaulin is securely pegged down.}{peg out the clothes before}
\vocabentry{534}{mow}{v.}{v. 刈，收割庄稼}{to cut plants, such as grass or wheat, that have long, thin stems and grow close together}{You can't mow the grass if it's wet.}{—}
\vocabentry{535}{deplete}{v.}{v. 耗尽，用尽}{to reduce something in size or amount, especially supplies of energy, money, etc.}{If we continue to deplete the earth's natural resources, we will cause serious damage to the environment.}{—}
\vocabentry{536}{detriment}{n.}{n. 损害，不利，伤害}{harm or damage}{Are you sure that I can follow this diet without detriment to my health?}{detriment to my health}
\vocabentry{537}{sprawl}{n.}{n. （城市）杂乱无序拓展的地区}{a position with the arms and legs spread out carelessly and untidily while sitting or lying down}{—}{—}
\vocabentry{538}{besiege}{v.}{v. 围攻}{to surround a place, especially with an army, to prevent people or supplies getting in or out}{The town had been besieged for two months but still resisted the aggressors.}{besiege for two months but}
\vocabentry{539}{practitioner}{n.}{n. （医生或律师等）从业者，从事者}{someone involved in a skilled job or activity}{Elizabeth Quan is a London-based practitioner of traditional Chinese medicine.}{practitioner of traditional Chinese medicine}
\vocabentry{540}{contingent}{n.}{n. 代表团}{a group of people representing an organization or country, or a part of a military force}{The French contingent certainly made their presence known at this year's conference.}{contingent of voluntary soldiers}
\vocabentry{541}{lucrative}{adj.}{adj. 有利可图的}{(especially of a business, job, or activity) producing a lot of money}{The merger proved to be very lucrative for both companies.}{lucrative for both companies}
\vocabentry{542}{breach}{v.}{v. 违反，违背}{to break a law, promise, agreement, or relationship}{They breached the agreement they had made with their employer.}{—}
\vocabentry{543}{assortment}{n.}{n. 各种各样的人（或物）}{a group of different types of something}{an assortment of vegetables}{assortment of vegetables}
\vocabentry{544}{paradigm}{n.}{n. 范例，示范}{a model of something, or a very clear and typical example of something}{Some of these educators are hoping to produce a change in the current cultural paradigm.}{—}
\vocabentry{545}{lavish}{adj.}{adj. 奢华的}{large in quantity and expensive or impressive}{lavish gifts / promises / praise}{—}
\vocabentry{546}{aide}{n.}{n. 助手}{a person whose job is to help someone important, such as a member of a government or a military officer of high rank}{a senior government aide}{aide to the prime minister}
\vocabentry{547}{discourse}{n.}{n. 话语，语篇}{the use of language to communicate in speech or writing, or an example of this}{Ellipsis is a characteristic feature of spoken discourse.}{—}
\vocabentry{548}{plight}{n.}{n. 困境}{an unpleasant condition, especially a serious, sad, or difficult one}{the plight of the poor / homeless}{plight of the poor /}
\vocabentry{549}{pharmacy}{n.}{n. 药房}{a shop or part of a shop in which medicines are prepared and sold}{—}{—}
\vocabentry{550}{volatile}{adj.}{adj. 不稳定的}{likely to change suddenly and unexpectedly, especially by getting worse}{Food and fuel prices are very volatile in a war situation.}{volatile in a war situation}
\vocabentry{551}{satire}{n.}{n. 讽刺（作品）}{a way of criticizing people or ideas in a humorous way, especially in order to make a political point, or a piece of writing that uses this style}{political satire}{satire on life in the}
\vocabentry{552}{tact}{n.}{n. 机智，得体，老练，圆滑}{the ability to say or do the right thing without making anyone unhappy or angry}{He's never had much tact and people don't like his blunt manner.}{—}
\vocabentry{553}{deplore}{v.}{v. 对……深感遗憾}{to say or think that something is very bad}{We deeply deplore the loss of life.}{—}
\vocabentry{554}{shred}{v.}{v. 切成细条，撕成碎片}{to cut or tear something roughly into thin strips}{Shred the lettuce and arrange it around the edge of the dish.}{—}
\vocabentry{555}{malignant}{adj.}{adj. （疾病）恶性的；恶毒的，充满恨意的}{A malignant disease or growth is cancer or is related to cancer, and is likely to be harmful}{The process by which malignant cancer cells multiply isn't fully understood.}{—}
\vocabentry{556}{maternal}{adj.}{adj. 母亲的，母性的}{behaving or feeling in the way that a mother does towards her child, especially in a kind, loving way}{maternal instincts}{—}
\vocabentry{557}{unprecedented}{adj.}{adj. 前所未有的，空前的，无前例的}{never having happened or existed in the past}{This century has witnessed environmental destruction on an unprecedented scale.}{—}
\vocabentry{558}{scenario}{n.}{n. （可能发生的）事态，情况}{a description of possible actions or events in the future}{There are several possible scenarios.}{—}
\vocabentry{559}{conducive}{adj.}{adj. 有益的，有助于……的}{providing the right conditions for something good to happen or exist}{Such a noisy environment was not conducive to a good night's sleep.}{conducive to a good night's}
\vocabentry{560}{livestock}{n.}{n. 家畜，牲畜}{animals and birds that are kept on a farm, such as cows, sheep, or chickens}{—}{—}
\vocabentry{561}{longevity}{n.}{n. 长寿，长命；寿命}{living for a long time}{To what do you attribute your longevity?}{—}
\vocabentry{562}{futile}{adj.}{adj. 无益的，无用的}{(of actions) having no effect or achieving nothing}{Attempts to get supplies to the region are futile because troops will not allow the aid convoy to enter the city.}{—}
\vocabentry{563}{celebrity}{n.}{n. 名人，名流}{someone who is famous, especially in the entertainment business}{Who was your first celebrity crush (= a celebrity you felt attracted to)?}{—}
\vocabentry{564}{indigenous}{adj.}{adj. 土生土长的，本土的}{used to refer to the people who originally lived in a place, rather than people who moved there from somewhere else, or to things that relate to these people}{So who are the indigenous people of this land?}{—}
\vocabentry{565}{yearn}{v.}{v. 渴望，向往}{to wish very strongly, especially for something that you cannot have or something that is very difficult to have}{Despite his great commercial success he still yearns for critical approval.}{yearn for critical approval}
\vocabentry{566}{salvation}{n.}{n. 拯救，救赎}{(a way of) being saved from danger, loss, or harm}{After the diagnosis, getting to know Mary was his salvation.}{—}
\vocabentry{567}{proofread}{v.}{v. 校正，校对}{to find and correct mistakes in text before it is printed or put online}{—}{—}
\vocabentry{568}{trophy}{n.}{n. 奖品，奖杯，奖牌}{a prize, such as a gold or silver cup, that is given to the winner of a competition or race, and often returned after a year to be given to the winner of the competition in the following year}{He's an excellent rider, but he's never won a major trophy.}{—}
\vocabentry{569}{poise}{v.}{v. 保持（某种姿势），使稳定}{calm confidence in a person's way of behaving, or a quality of grace (= moving in an attractive way) and balance in the way a person holds or moves their body}{He looked embarrassed for a moment, then quickly regained his poise.}{—}
\vocabentry{570}{salvage}{vt.}{vt. 打捞}{to save goods from damage or destruction, especially from a ship that has sunk or been damaged or a building that has been damaged by fire or a flood}{gold coins salvaged from a shipwreck}{salvage from a shipwreck}
\vocabentry{571}{contagious}{adj.}{adj. 有感染力的}{A contagious disease can be caught by touching someone who has the disease or by touching an infected object, or by an infected person coughing, sneezing, etc. near you}{The infection is highly contagious, so don't let anyone else use your towel.}{—}
\vocabentry{572}{ardent}{adj.}{adj. 热心的，热烈的}{showing strong feelings}{an ardent supporter of Manchester United}{—}
\vocabentry{573}{juvenile}{n.}{n. 青少年}{a person who is not old enough to be considered an adult}{He was still a juvenile when the crime was committed.}{juvenile to adult correctional systems}
\vocabentry{574}{brigade}{n.}{n. 队列，大部队，旅}{a large group of soldiers in an army}{—}{—}
\vocabentry{575}{stroll}{n.}{n. 漫步，散步}{a slow relaxed walk, especially for pleasure}{After dinner, we went for a stroll along the beach.}{stroll along the beach}
\vocabentry{576}{akin}{adj.}{adj. 类似的}{having some of the same qualities}{They speak a language akin to French.}{akin to French}
\vocabentry{577}{aggregate}{adj.}{adj. 总计的，集合的}{total}{The seven companies have an aggregate turnover of £5.2 million.}{—}
\vocabentry{578}{chronicle}{v.}{v. 记录，把……载入编年史}{to make a record or give details of something}{The book chronicles the writer's coming to terms with his illness.}{—}
\vocabentry{579}{syndrome}{n.}{n. 【医】综合症}{a combination of medical problems that shows the existence of a particular disease or mental condition}{Early diagnosis of the syndrome is difficult, but it is important to begin treatment as soon as possible.}{—}
\vocabentry{580}{flirt}{vi.}{vi. 戏弄，不认真地对待}{to behave as if sexually attracted to someone, although not seriously}{Christina was flirting with just about every man in the room.}{flirt with just about every}
\vocabentry{581}{subsistence}{n.}{n. 自给自足}{the state of having what you need in order to stay alive, but no more}{The money is intended to provide a basic subsistence and should not be paid to someone who receives other income.}{—}
\vocabentry{582}{airborne}{adj.}{adj. 在空中的}{in the air, or carried by air or wind or by an aircraft}{The airborne radioactive particles have covered a huge area of Russia.}{—}
\vocabentry{583}{ration}{n.}{n. 定量配给}{a limited amount of something that one person is allowed to have, especially when there is not much of it available}{During the war, no one was allowed more than their ration of food, clothing and fuel.}{rations [ plural ]：the total amount of food that is given to someone to be eaten during a particular activity and in a particular period of time, especially an amount given to soldiers when they are fighting: Rations were frequently allocated in public to ensure fairness.}
\vocabentry{584}{legacy}{n.}{n. 遗产；遗留问题}{money or property that you receive from someone after they die}{An elderly cousin had left her a small legacy.}{—}
\vocabentry{585}{stifle}{v.}{v. 抑制，压制，使窒息}{to (cause to) be unable to breathe because you have no air}{He is said to have stifled his victim with a pillow.}{stifle in the heat of}
\vocabentry{586}{feat}{n.}{n. 绝技，功绩，武艺}{something difficult needing a lot of skill, strength, courage, etc. to achieve it}{The Eiffel Tower is a remarkable feat of engineering.}{feat of engineering}
\vocabentry{587}{tread}{v.}{v. （小心）行事}{to put your foot on something or to press something down with your foot}{I kept treading on his toes when we were dancing.}{tread water：to float vertically in the water by moving the legs and the arms up and down: I stopped swimming for a moment and trod water, looking back to the beach.}
\vocabentry{588}{soothe}{v.}{v. 使（某人、情绪）平静}{to make someone feel calm or less worried}{to soothe a crying baby}{—}
\vocabentry{589}{catastrophe}{n.}{n. 大灾难}{a sudden event that causes very great trouble or destruction}{They were warned of the ecological catastrophe to come.}{catastrophe to come}
\vocabentry{590}{enlist}{v.}{v. 招募}{to join the armed forces}{They both enlisted (in the navy) a year before the war broke out.}{—}
\vocabentry{591}{peninsula}{n.}{n. 半岛}{a long piece of land that sticks out from a larger area of land into the sea or into a lake}{the Korean/ Arabian /Florida Peninsula}{—}
\end{description}
\end{document}
